### 2021-03-10 papers/sbst21/paper_sbst21.tex
Paper for 21

%--------1---------2---------3---------4---------5---------6---------7
%
% Competition paper
% SBST 2013
% Page limit: 4 pages
%

%\documentclass[10pt, conference, compsocconf]{IEEEtran}
%\documentclass[10pt,conference,compsocconf]{IEEEtran}
\documentclass[10pt,conference]{IEEEtran}

%\documentclass[times, 10pt,twocolumn]{article} 
%\usepackage{latex8}
%\usepackage{times}
\usepackage{amsfonts}
\usepackage[latin1]{inputenc}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{algorithmic}
\usepackage{float}
\usepackage[numbers,sort&compress,square]{natbib}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{subfigure}
%\usepackage{hyperref}
\usepackage{color}
\usepackage[usenames,dvipsnames,table]{xcolor}
\usepackage{soul}
\usepackage{xspace}
\usepackage{boxedminipage}
\usepackage{alltt}
\usepackage{multirow}
\usepackage{paralist}
\usepackage{amsmath}
\usepackage{balance}
\definecolor{light-gray}{gray}{0.90}

\floatstyle{ruled}
\newfloat{algorithm}{tbp}{loa}
\floatname{algorithm}{Algorithm}

\newtheorem{definition}{Definition}

 %krams hinter fontadjust ist neu
  \definecolor{lightgrey}{rgb}{0.90,0.90,0.90}
\lstset{escapeinside={(*}{*)}}
  \lstloadlanguages{java}
 \lstdefinelanguage{pseudocode}
  {morekeywords={if, else, initialize, return, for, each, in, global, new}
   }
  \lstset{
    tabsize=2,
    mathescape=true,
    escapeinside={(*}{*)},
    captionpos=t,
    framerule=0pt,
    backgroundcolor=\color{lightgrey},
    basicstyle=\scriptsize\ttfamily,
    keywordstyle=\footnotesize\bfseries,
    numbers=none,
    numberstyle=\tiny,
    numbersep=1pt,
    fontadjust,
    breaklines=true,
    breakatwhitespace=false
  }

% \hypersetup{
% colorlinks=true,
% urlcolor=rltblue,
% linkcolor=rltred,
% citecolor=rltgreen,
% bookmarksnumbered=true,
% pdftitle={EvoSuite at the SBST 2016 Tool Competition},
% pdfauthor={Gordon Fraser and Andrea Arcuri},
% pdfsubject={Test case generation},
% pdfkeywords={Test case generation, unit testing, test
%   oracles, assertions, search based testing}
% }

\definecolor{rltred}{rgb}{0.5,0,0}
\definecolor{rltgreen}{rgb}{0,0.5,0}
\definecolor{rltblue}{rgb}{0,0,0.5}
\definecolor{ScarletRed}{rgb}{0.80,0.00,0.00}

% in draft mode we put \remarks into the margins and do other stuff
% set to \draftfalse for 
\newif\ifdraft
\draftfalse

\ifdraft
	\marginparwidth=1.3cm
	\marginparsep=5pt
	\newcommand\remark[1]{%
		\mymarginpar{\raggedright\hbadness=10000\tiny\it #1\par}}
	% TODO marker
	\newcommand{\TODO}[1]{\sethlcolor{yellow}\textbf{\textcolor{ScarletRed}{\hl{TODO: #1}}}\xspace}
\else
	\newcommand\remark[1]	{}
	\newcommand{\TODO}[1]{}
\fi

\ifdraft
	\overfullrule3pt
\fi

% We use \FIXME for located problems (``defect'')
\newcommand{\FIXME}[1]{\remark{FIXME: #1}}
\newcommand\parremark[1]	{\par\textbf{REMARK:} #1\par}

\newcommand{\gordon}[1]{\textcolor{blue}{\sf\small\textbf{Gordon:} #1}}
\newcommand{\andrea}[1]{\textcolor{ScarletRed}{\sf\small\textbf{Andrea:} #1}}

% \mathid is used to denote identifiers and slots in formulas
\newcommand{\mathid}[1]{\text{\rmfamily\textit{#1}}}

% But usually, we shall use \|name| instead.
\def\|#1|{\mathid{#1}}

% \codeid is used to denote computer code identifiers
\newcommand{\codeid}[1]{\texttt{#1}}

% But usually, we shall use \<name> instead.
\def\<#1>{\codeid{#1}}

% Our results
\newenvironment{result}%
{\smallskip
\noindent
\let\emph=\textbf
\begin{boxedminipage}{\columnwidth}\begin{center}\em}%
{\end{center}\end{boxedminipage}%
\smallskip
}

\newcommand{\JodaTime}{Joda-Time\xspace}  % That's how they write themselves -- AZ

\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
\newcommand{\JTEXPERT}{{\sc jTExpert}\xspace}
\newcommand{\RANDOOP}{{\sc Randoop}\xspace}
\newcommand{\TT}{{\sc T3}\xspace}

\newcommand{\MUTEST}{{\sc $\mu$Test}\xspace}
\newcommand{\CS}{{\sc SF100}\xspace}

\DeclareMathSymbol{,}{\mathpunct}{letters}{"3B}
\DeclareMathSymbol{,}{\mathord}{letters}{"3B}
\DeclareMathSymbol{\decimal}{\mathord}{letters}{"3A}
%%%"

%\input{macros}

%------------------------------------------------------------------------- 
% take the % away on next line to produce the final camera-ready version 
%\pagestyle{empty}

%------------------------------------------------------------------------- 
\begin{document}

%

%\title{Unit Testing Tool competition: Results for EvoSuite}
\title{\EVOSUITE at the SBST 2021 Tool Competition}

\author{%
%
\IEEEauthorblockN{%
Sebastian Vogl\IEEEauthorrefmark{1}, 
Sebastian Schweikl\IEEEauthorrefmark{1},
Gordon Fraser\IEEEauthorrefmark{1}, 
Andrea Arcuri\IEEEauthorrefmark{2},
Jose Campos\IEEEauthorrefmark{3},
and Annibale Panichella\IEEEauthorrefmark{4}%
}
%
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Passau, Germany\\
\{sebastian.vogl,sebastian.schweikl,gordon.fraser\}@uni-passau.de}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College, Norway\\andrea.arcuri@kristiania.no}
\IEEEauthorblockA{\IEEEauthorrefmark{3}University of Lisbon, Portugal\\jcmcampos@fc.ul.pt}
\IEEEauthorblockA{\IEEEauthorrefmark{4}Delft University of Technology, Netherlands\\A.Panichella@tudelft.nl}%
}

\maketitle
%\thispagestyle{empty}

\begin{abstract}
  \EVOSUITE is a search-based unit test generation tool for Java. This paper summarises the results and experiences of \EVOSUITE's participation at the ninth unit testing competition at SBST 2021, where \EVOSUITE achieved the highest overall score.
\end{abstract}

%------------------------------------------------------------------------- 
\section{Introduction}
%
The annual unit test generation competition aims to drive and evaluate progress
on unit test generation tools. Every year, a benchmark of Java classes is
selected, and different test generation tools are evaluated in terms of the
code coverage and mutation scores they can achieve on these classes. In the
2021 edition of the competition, six tools were applied on a set of 98 classes.
Details about the procedure of the competition, the technical framework, and
the benchmark classes can be found in the competition report~\cite{SBST:2021}.
\EVOSUITE achieved an overall score of 292.05, which was the highest among the
competing and baseline tools.

%------------------------------------------------------------------------- 
\section{About EvoSuite}

\EVOSUITE~\cite{FrA11c} uses evolutionary search to automatically generate test
suites for Java classes. It takes as input the name of a target class as well
as the classpath containing the compiled bytecode of the class as well as its
dependencies. A basic static analysis extracts information about the relevant
classes as well as their constructors, methods, and fields. The bytecode is
instrumented while classes are loaded, such that \EVOSUITE can produce
execution traces for test executions, and to avoid test flakiness by replacing
non-deterministic calls with deterministic, mocked versions. \EVOSUITE then
applies meta-heuristic search algorithms to automatically produce a set of JUnit
test cases aimed at maximising code coverage. 
%Besides the basic command line interface there are also plugins for popular development environments such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.

Originally, \EVOSUITE was implemented to optimise entire test suites with
respect to their overall code coverage~\cite{GoA_TSE12}. The latest search algorithm, which is now used by default, is the \textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search algorithm~\cite{dynamosa} which operates at the test case level. 
%
The genetic encoding of test cases in \EVOSUITE consists of variable-length sequences of Java statements (e.g., primitive statements as well as calls on constructors or methods). Standard evolutionary search operators (e.g., selection, crossover, mutation) are adapted for this representation. 
%
\EVOSUITE supports multiple different coverage criteria that can be optimised simultaneously. The core fitness functions in \EVOSUITE are based on traditional heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details). Further criteria include mutation testing~\cite{emse14_mutation} as well as other basic
criteria~\cite{rojas2015combining}.

To improve the readability of the generated tests, \EVOSUITE applies post-processing once the available search budget has been exhausted~\cite{FrA11c,FrA13a}. In particular, minimisation is used to remove redundant tests and statements, and a minimised set of assertions is added using mutation analysis~\cite{10.1109/TSE.2011.93}. Finally, \EVOSUITE compiles and executes each test individually to avoid compile errors (which may be the result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the class under test.

%Besides multiple in-depth empirical evaluations of \EVOSUITE with respect to
%code coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa},
%fault-finding effectiveness~\cite{shamshiri2015automatically,moein2017}, and
%effects on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and
%software maintenance~\cite{ICST2018_Maintenance}, \EVOSUITE has also participated in all prior instances of the unit testing tool competition, usually ranking among the best performing tools.

%------------------------------------------------------------------------- 
\section{Competition Setup}

The most recent version of \EVOSUITE (1.1.0) was used in the competition. As of
this version the default search algorithm in \EVOSUITE is
DynaMOSA~\cite{dynamosa}. No new features were added in this version, but
support for Java 9+ was added, several bugs were fixed, and a major refactoring
was applied to improve the code quality with respect to the use of Java
generics internally. Several smaller bugfixes were applied in the run-up to the
competition, which are now included in the current development version on
GitHub.

The configuration of \EVOSUITE used in the 2021 competition is identical to the
configuration used in prior years, and largely based on its tuned default
values~\cite{arcuri2013parameter} and default coverage criteria
\cite{rojas2015combining}.
%
Similar to prior competitions, the test minimisation step was omitted as the competition score does not reward test minimality, and the minimisation takes substantial computational effort. Similarly, we included all regression assertions rather than filtering them with mutation analysis to save time. 
%
Same as in previous competitions, we allocated 50\% of
the overall time set by the competition organisers for the search, and
distributed the other 50\% equally to the remaining phases (e.g., assertion generation, compile-check, flakiness-check).

%------------------------------------------------------------------------- 
\section{Results}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{CoverageBoxV}
	\caption{\label{fig:results}Coverage results achieved in the competition.}
\end{figure}

With an overall score of 292.05, \EVOSUITE achieved the highest score of all
tools in the competition. As described in the competition
report~\cite{SBST:2021}, the score is calculated on the subset of 25 classes
for which all tools produced tests in some of the runs.
Figure~\ref{fig:results} summarises the results of \EVOSUITE in terms of the
mean coverage for the 25 classes used in the competition. While the coverage
increased from the 30 seconds to the 120 seconds search budget (mean line
coverage of 65.7\% vs. 77.1\%, respectively), the additional run of 300 seconds
actually shows a slight decrease (mean line coverage of 73.9\%). The likely
reason for this result is that \EVOSUITE crashed more frequently when given
more time. For example, for 76 runs of \EVOSUITE on the 25 classes no test
cases were generated. In the majority of these cases we found that the JVM
process running \EVOSUITE on the competition machine crashed with an
\texttt{OutOfMemoryException}, which possibly could have been avoided with a
more generous allocation of memory.

The coverage ratios are generally higher than the mutation scores; while this is largely because it is simply more difficult to achieve a high mutation score, the mutation score is also negatively affected by classes with flakiness or failing tests (in which case the mutation score reported is 0\% by definition). Furthermore, in many cases the execution with the PIT mutation tool reported an error during class loading, which may be caused by configuration errors or clashes between \EVOSUITE's and PIT's bytecode instrumentation.

A final observation is that all 25 Java classes considered in the competition
results were taken from the Guava project, which is notorious for its complex
use of Java Generics---which is a feature \EVOSUITE still struggles to handle
effectively. In particular, in 99 of all runs on the 25 competition classes
\EVOSUITE did not manage to move beyond the initial generation, which tends to
happen specifically when \EVOSUITE struggles to correctly instantiate complex,
nested generic types. This is currently a focus point of structural
improvements and refactorings in \EVOSUITE's codebase.

%------------------------------------------------------------------------- 
\section{Conclusions}

This paper reports on the participation of the \EVOSUITE test generation tool
in the 9th SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
71\% branch coverage, 77\% line coverage, and a mutation score of 53\%, using a
search budget of 120 seconds on the 25 classes considered for the competition.
Overall, this results in a score of 292.05, which is the highest score of all
tools in the competition.

To learn more about \EVOSUITE, visit our Web site:
\begin{center}
%\url{http://evosuite.org/}
\texttt{http://www.evosuite.org}
\end{center}

%-------------------------------------------------------------------------

%\noindent
\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
This project has been funded by the EPSRC project ``GREATEST'' (EP/N023978/2).

%------------------------------------------------------------------------- 
%\def\IEEEbibitemsep{5pt plus 1pt}
%\def\IEEEbibitemsep{6pt}
%\clearpage
\bibliographystyle{IEEEtranS}
\bibliography{papers}
\balance

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2021-03-11 plots/create_coverage_boxplot.py
script to generate plot for the 2021 paper

@@ -1,0 +1,81 @@
+"""
+Generate a boxplot for the distributions of line coverage, branch coverage and mutants killed.
+
+This script requires one csv-Files to load the results from the SBST-tool competition for every budget.
+
+You can generate such a csv-file from the provided zip-File by:
+
+# unzip evosuite_results_30.zip
+# cd evosuite_results_30
+# head -1 <ANY_BENCHMARK_FOLDER>/metrics/transcript.csv > metrics.csv
+# find -wholename "*/metrics/transcript.csv" -exec sed -n 2p {} \; >> metrics.csv
+
+This will generate a metrics.csv in the results-folder as needed by this script.
+Generate the csv-File for every budget.
+"""
+
+import pandas as pd
+import seaborn as sns
+import matplotlib.pyplot as plt
+sns.set_style("whitegrid")
+
+"""
+List of tuples to specify the location and search budgets to be used.
+Every tuple must contain of 3 elements: (int, str, file_path)
+
+The first element is used to order the boxes.
+The second element is used in the legend of the box plot for the given dataset.
+The thrid element is the file_path to the data set
+"""
+data_sets = [
+    (30, "30s", "results_evosuite_30/metrics.csv"),
+    (120, "120s", "results_evosuite_120/metrics.csv"),
+    (300, "300s", "results_evosuite_300/metrics.csv")
+]
+
+output_file_name = "CoverageBoxV.pdf"
+
+
+def load_data_set(data_set):
+    data = pd.read_csv(data_set[2])
+    data["budget"] = data_set[0]
+    return data
+
+
+metrics = [x for x in map(load_data_set, data_sets)]
+means = [x for x in map(lambda x: x.groupby("benchmark").mean().reset_index(), metrics)]
+
+metrics_all = pd.concat(metrics)
+means_all = pd.concat(means)
+
+
+def plot_whole_coverage_v(df, cols=None,
+                          save_as="",
+                          palette=None,
+                          labels=None,
+                          xticklabels=None):
+    if cols is None:
+        cols = ["linesCoverageRatio", "conditionsCoverageRatio", "mutantsCoverageRatio"]
+    if xticklabels is None:
+        xticklabels = ["Lines Covered", "Branches Covered", "Mutants Killed"]
+    if not palette:
+        palette = sns.color_palette()
+    fig = plt.figure(figsize=(7, 5))
[…]

### 2022-03-04 papers/sbst22/paper_sbst22.tex
Copy paper from last year

--- 2021-03-10 papers/sbst21/paper_sbst21.tex
@@
 %--------1---------2---------3---------4---------5---------6---------7
-%
-% Competition paper
-% SBST 2013
-% Page limit: 4 pages
-%
 
@@
 \{sebastian.vogl,sebastian.schweikl,gordon.fraser\}@uni-passau.de}
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College, Norway\\andrea.arcuri@kristiania.no}
+\IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College and Oslo Metropolitan University, Norway\\andrea.arcuri@kristiania.no}
 \IEEEauthorblockA{\IEEEauthorrefmark{3}University of Lisbon, Portugal\\jcmcampos@fc.ul.pt}
@@
 suites for Java classes. It takes as input the name of a target class as well
-as the classpath containing the compiled bytecode of the class as well as its
-dependencies. A basic static analysis extracts information about the relevant
-classes as well as their constructors, methods, and fields. The bytecode is
-instrumented while classes are loaded, such that \EVOSUITE can produce
-execution traces for test executions, and to avoid test flakiness by replacing
-non-deterministic calls with deterministic, mocked versions. \EVOSUITE then
-applies meta-heuristic search algorithms to automatically produce a set of JUnit
-test cases aimed at maximising code coverage. 
+as the classpath describing where the compiled bytecode of the class as well as
+its dependencies are located. A basic static analysis extracts information
+about the relevant classes as well as their constructors, methods, and fields.
+The bytecode is instrumented while classes are loaded, such that \EVOSUITE can
+produce execution traces for test executions, and to avoid test flakiness by
+replacing non-deterministic calls with deterministic, mocked versions.
+\EVOSUITE then applies meta-heuristic search algorithms to automatically
+produce a set of JUnit test cases aimed at maximising code coverage.
 %Besides the basic command line interface there are also plugins for popular development environments such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.
@@
 The core fitness functions in \EVOSUITE are based on traditional heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details).
-Further criteria include mutation testing~\cite{emse14_mutation} as well as other basic
-criteria~\cite{rojas2015combining}.
+Further fitness functions are based on mutation testing~\cite{emse14_mutation} as well as other basic criteria~\cite{rojas2015combining}.
 
-To improve the readability of the generated tests, \EVOSUITE applies post-processing once the available search budget has been exhausted~\cite{FrA11c,FrA13a}.
+To improve the readability of the generated tests and to avoid test smells~\cite{panichella2020revisiting}, \EVOSUITE applies post-processing once the available search budget has been exhausted~\cite{FrA11c,FrA13a}.
 In particular, minimisation is used to remove redundant tests and statements, and a minimised set of assertions is added using mutation analysis~\cite{10.1109/TSE.2011.93}.
-Finally, \EVOSUITE compiles and executes each test individually to avoid compile errors (which may be the result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the class under test.
+Finally, \EVOSUITE compiles and executes each test individually to avoid compilation errors (which may be the result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the class under test.
 
@@
 The most recent version of \EVOSUITE (1.1.0) was used in the competition. As of
-this version the default search algorithm in \EVOSUITE is
+this version, the default search algorithm in \EVOSUITE is
 DynaMOSA~\cite{dynamosa}. No new features were added in this version, but
@@
 	\includegraphics[width=\columnwidth]{CoverageBoxV}
+	\vspace{-2em}
 	\caption{\label{fig:results}Coverage results achieved in the competition.}
+	\vspace{-1em}
 \end{figure}
@@
 more time. For example, for 76 runs of \EVOSUITE on the 25 classes no test
-cases were generated. In the majority of these cases we found that the JVM
-process running \EVOSUITE on the competition machine crashed with an
+cases were generated. In most cases we found that the JVM process running
+\EVOSUITE on the competition machine crashed with an
 \texttt{OutOfMemoryException}, which possibly could have been avoided with a
@@
 This paper reports on the participation of the \EVOSUITE test generation tool
-in the 9th SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
+in the ninth SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
 71\% branch coverage, 77\% line coverage, and a mutation score of 53\%, using a
@@
 %\noindent
-\textbf{Acknowledgments:} Many thanks to all the contributors to \EVOSUITE.
-This project has been funded by the EPSRC project ``GREATEST'' (EP/N023978/2).
+\textbf{Acknowledgments:} Many thanks to all the contributors to
+\EVOSUITE.
+This project has been supported by EPSRC project % ``GREATEST'' 
+EP/N023978/2.
 

### 2022-03-04 papers/sbst22/data/main.py
Add analysis script

@@ -1,0 +1,111 @@
+#!/usr/bin/env python
+
+import pandas as pd
+import utils
+
+all_data = pd.read_csv('./results.csv')
+
+coverage_columns = ['linesCoverageRatio',
+                    'conditionsCoverageRatio',
+                    'mutantsCoverageRatio']
+
+translation = ['Lines Covered', 'Branches Covered', 'Mutants Killed']
+
+columns = {
+    'timeBudget': 'Time Budget',
+    **dict(zip(coverage_columns, translation))
+}
+
+"""
+(1) Remove all data not related to EvoSuite and only keep the relevant columns
+(2) Rename the columns to give them more descriptive names
+(3) Reshape the data such that the "Time Budget" is used as identifier, and the
+    remaining columns are "un-pivoted":
+
+          Time Budget          Metric     Percent
+    0              30   Lines Covered    0.000000
+    1              30   Lines Covered   20.833332
+    ...           ...             ...         ...
+    3898          120  Mutants Killed   55.882350
+    3899          120  Mutants Killed    0.000000
+"""
+plot_data = (all_data[columns.keys()]  # (1)
+             .rename(columns=columns)  # (2)
+             .melt(id_vars='Time Budget',
+                   var_name='Metric',
+                   value_name='Percent'))  # (3)
+
+"""
+Create a boxplot of the EvoSuite data per "Metric" on the x-axis, plotting the 
+corresponding values in the "Percent" column on the y-axis. Using "Time Budget"
+as hue key creates grouped a boxplot: for each metric, it actually plots two 
+boxes for the two budgets.
+"""
+utils.preload_latex_style()
+fig, ax = utils.boxplot(data=plot_data,
+                        x='Metric',
+                        y='Percent',
+                        hue='Time Budget',
+                        title='Time Budget [s]',
+                        figsize=(3.5, 2.15))
+utils.save_fig(fig, './CoverageBoxV.pdf')
+
+
+def budget(seconds):
+    return all_data['timeBudget'] == seconds
+
+
+data30 = all_data[budget(30)]
+data120 = all_data[budget(120)]
+
+stats = {
+    'score': 380.57,
+    'cuts': all_data['class'].nunique(),
+    'budgetShort': r'\SI{30}{\second}',
+    'budgetLong': r'\SI{120}{\second}',
+}
+
+
+def my_capitalize(s):
+    return s[0].upper() + s[1:]
+
+
[…]

### 2022-03-04 papers/sbst22/data/utils.py

@@ -1,0 +1,93 @@
+import seaborn as sns
+import matplotlib.pyplot as plt
+
+
+def boxplot(data, x, y, hue, title=None, figsize=None):
+    if title is None:
+        title = hue
+
+    n_colors = data[hue].nunique()
+
+    def style_axes():
+        # Enlarge the range of the y-axis. Otherwise, whiskers at 0% or 100% are
+        # not visible.
+        ax.set_ylim(-5, 105)
+        all_axes = {'top': True, 'right': True, 'left': True, 'bottom': True}
+        sns.despine(fig, ax, **all_axes)
+
+    def set_legend():
+        # Remove the label from the x-axis. We create a separate "legend box"
+        # instead.
+        ax.set_xlabel('')
+        center_legend_below_plot = {
+            'loc': 'lower center',
+            'bbox_to_anchor': (0.5, -0.5)
+        }
+        ax.legend(title=title,
+                  ncol=n_colors,
+                  **center_legend_below_plot)
+
+    # Create a grouped boxplot using the supplied data. "x" is the column name
+    # of the data to plot on the x-axis, and "y" is the column name of the data
+    # to plot on the y-axis. The "hue" determines the subgroups.
+    fig = plt.figure(figsize=figsize)
+    palette = sns.color_palette(palette='pastel', n_colors=n_colors)
+    ax = sns.boxplot(data=data, x=x, y=y, hue=hue, palette=palette,
+                     linewidth=0.5)
+
+    style_axes()
+
+    # Display a legend below the plot, also giving the x-axis a label
+    # (or "title"). The main purpose of the legend is to distinguish the boxes
+    # within a grouped boxplot via their color.
+    set_legend()
+
+    return fig, ax
+
+
+def save_fig(fig, filename):
+    # Save the plot as a PDF. Without bbox_inches='tight', the legend is missing
+    # in the PDF...
+    fig.savefig(filename, filetype='pdf', bbox_inches='tight', backend='pgf')
+
+
+def preload_latex_style():
+    plt.style.use('seaborn')
+    sns.set_style('whitegrid', {'grid.linewidth': 52})
+    sns.set_context('paper')
+    load_custom_font = '\n'.join([
+        r'\usepackage{newtxtext,newtxmath}',
+        r'\usepackage[T1]{fontenc}',
+    ])
+    plt.rcParams.update({
+        'text.usetex': True,
+        'pgf.texsystem': 'pdflatex',
[…]

### 2022-03-04 papers/sbst22/paper_sbst22.tex
Update data in paper

@@
 
-\newcommand{\EVOSUITE}{{\sc EvoSuite}\xspace}
-\newcommand{\JTEXPERT}{{\sc jTExpert}\xspace}
-\newcommand{\RANDOOP}{{\sc Randoop}\xspace}
-\newcommand{\TT}{{\sc T3}\xspace}
+\newcommand{\EVOSUITE}{\textsc{EvoSuite}\xspace}
+\newcommand{\JTEXPERT}{\textsc{jTExpert}\xspace}
+\newcommand{\RANDOOP}{\textsc{Randoop}\xspace}
+\newcommand{\TT}{\textsc{T3}\xspace}
 
@@
 
-%\input{macros}
+\usepackage{siunitx}
+\input{data/macros}
 
@@
 %\title{Unit Testing Tool competition: Results for EvoSuite}
-\title{\EVOSUITE at the SBST 2021 Tool Competition}
+\title{\EVOSUITE at the SBST 2022 Tool Competition}
 
@@
 \IEEEauthorblockN{%
-Sebastian Vogl\IEEEauthorrefmark{1}, 
 Sebastian Schweikl\IEEEauthorrefmark{1},
@@
   \EVOSUITE is a search-based unit test generation tool for Java.
-This paper summarises the results and experiences of \EVOSUITE's participation at the ninth unit testing competition at SBST 2021, where \EVOSUITE achieved the highest overall score.
+This paper summarises the results and experiences of \EVOSUITE's participation at the 10th unit testing competition at SBST 2022, where \EVOSUITE achieved the highest overall score.
 \end{abstract}
@@
 code coverage and mutation scores they can achieve on these classes. In the
-2021 edition of the competition, six tools were applied on a set of 98 classes.
+2022 edition of the competition, seven tools were applied on a set of \cuts classes.
 Details about the procedure of the competition, the technical framework, and
-the benchmark classes can be found in the competition report~\cite{SBST:2021}.
-\EVOSUITE achieved an overall score of 292.05, which was the highest among the
+the benchmark classes can be found in the competition report~\cite{SBST-toolcomp22}.
+\EVOSUITE achieved an overall score of \score, which was the highest among the
 competing and baseline tools.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{CoverageBoxV}
+	\includegraphics[width=\columnwidth]{data/CoverageBoxV}
 	\vspace{-2em}
@@
 
-With an overall score of 292.05, \EVOSUITE achieved the highest score of all
+With an overall score of \score, \EVOSUITE achieved the highest score of all
 tools in the competition. As described in the competition
-report~\cite{SBST:2021}, the score is calculated on the subset of 25 classes
+report~\cite{SBST-toolcomp22}, the score is calculated on the subset of \cuts classes
 for which all tools produced tests in some of the runs.
 Figure~\ref{fig:results} summarises the results of \EVOSUITE in terms of the
-mean coverage for the 25 classes used in the competition. While the coverage
-increased from the 30 seconds to the 120 seconds search budget (mean line
-coverage of 65.7\% vs. 77.1\%, respectively), the additional run of 300 seconds
+mean coverage for the \cuts classes used in the competition. While the coverage
+increased from the \budgetShort to the \budgetLong search budget (mean line
+coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively),
+the additional run of 300 seconds
 actually shows a slight decrease (mean line coverage of 73.9\%). The likely
 reason for this result is that \EVOSUITE crashed more frequently when given
-more time. For example, for 76 runs of \EVOSUITE on the 25 classes no test
+more time. For example, for 76 runs of \EVOSUITE on the \cuts classes no test
 cases were generated. In most cases we found that the JVM process running
@@
 
-A final observation is that all 25 Java classes considered in the competition
+A final observation is that all \cuts Java classes considered in the competition
 results were taken from the Guava project, which is notorious for its complex
 use of Java Generics---which is a feature \EVOSUITE still struggles to handle
-effectively. In particular, in 99 of all runs on the 25 competition classes
+effectively. In particular, in 99 of all runs on the \cuts competition classes
 \EVOSUITE did not manage to move beyond the initial generation, which tends to
@@
 This paper reports on the participation of the \EVOSUITE test generation tool
-in the ninth SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
-71\% branch coverage, 77\% line coverage, and a mutation score of 53\%, using a
-search budget of 120 seconds on the 25 classes considered for the competition.
-Overall, this results in a score of 292.05, which is the highest score of all
+in the tenth SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
+\avgConditionsCoverageRatioLong branch coverage, \avgLinesCoverageRatioLong line coverage, 
+and a mutation score of \avgMutantsCoverageRatioLong, using a
+search budget of \budgetLong on the \cuts classes considered for the competition.
+Overall, this results in a score of \score, which is the highest score of all
 tools in the competition.

### 2022-03-04 papers/sbst22/data/main.py
Plots grouped by benchmark per search budget

@@ -42,12 +42,13 @@ as hue key creates grouped a boxplot: for each metric, it actually plots two
 boxes for the two budgets.
 """
 utils.preload_latex_style()
-fig, ax = utils.boxplot(data=plot_data,
-                        x='Metric',
-                        y='Percent',
-                        hue='Time Budget',
-                        title='Time Budget [s]',
-                        figsize=(3.5, 2.15))
+
+fig = utils.boxplot(data=plot_data,
+                    x='Metric',
+                    y='Percent',
+                    hue='Time Budget',
+                    title='Time Budget [s]',
+                    figsize=(3.5, 2.15))
 utils.save_fig(fig, './CoverageBoxV.pdf')
 
 
@@ -57,6 +58,46 @@ def budget(seconds):
 
 data30 = all_data[budget(30)]
 data120 = all_data[budget(120)]
+
+
+def benchmark_basename(benchmark_name):
+    return benchmark_name.split('-')[0].capitalize()
+
+
+columns = {
+    'benchmark': 'Benchmark',
+    **dict(zip(coverage_columns, translation))
+}
+
+data_by_benchmark30 = (data30[['benchmark', *coverage_columns]]
+                       .rename(columns=columns)
+                       .melt(id_vars='Benchmark',
+                             var_name='Metric',
+                             value_name='Percent'))
+benchmarks = data_by_benchmark30['Benchmark'].copy()
+data_by_benchmark30['Benchmark'] = benchmarks.map(benchmark_basename)
+
+fig = utils.boxplot(data=data_by_benchmark30,
+                    x='Metric',
+                    y='Percent',
+                    hue='Benchmark',
+                    figsize=(3.5, 2.15))
+utils.save_fig(fig, './CoverageByBenchmark30.pdf')
+
+data_by_benchmark120 = (data120[['benchmark', *coverage_columns]]
+                        .rename(columns=columns)
+                        .melt(id_vars='Benchmark',
+                              var_name='Metric',
+                              value_name='Percent'))
+benchmarks = data_by_benchmark120['Benchmark'].copy()
+data_by_benchmark120['Benchmark'] = benchmarks.map(benchmark_basename)
+
+fig = utils.boxplot(data=data_by_benchmark120,
+                    x='Metric',
+                    y='Percent',
+                    hue='Benchmark',
+                    figsize=(3.5, 2.15))
+utils.save_fig(fig, './CoverageByBenchmark120.pdf')
 
 stats = {
     'score': 380.57,

### 2022-03-04 papers/sbst22/data/utils.py

@@ -32,8 +32,9 @@ def boxplot(data, x, y, hue, title=None, figsize=None):
     # to plot on the y-axis. The "hue" determines the subgroups.
     fig = plt.figure(figsize=figsize)
     palette = sns.color_palette(palette='pastel', n_colors=n_colors)
+    flierprops = {'marker': 'o', 'markersize': 1.0}
     ax = sns.boxplot(data=data, x=x, y=y, hue=hue, palette=palette,
-                     linewidth=0.5)
+                     linewidth=0.5, flierprops=flierprops)
 
     style_axes()
 
@@ -42,7 +43,7 @@ def boxplot(data, x, y, hue, title=None, figsize=None):
     # within a grouped boxplot via their color.
     set_legend()
 
-    return fig, ax
+    return fig
 
 
 def save_fig(fig, filename):

### 2022-03-07 papers/sbst22/data/main.py
Generate graphics using the correct fonts

@@ -41,7 +41,7 @@ corresponding values in the "Percent" column on the y-axis. Using "Time Budget"
 as hue key creates grouped a boxplot: for each metric, it actually plots two 
 boxes for the two budgets.
 """
-utils.preload_latex_style()
+utils.preload_latex_style("ACM")
 
 fig = utils.boxplot(data=plot_data,
                     x='Metric',

### 2022-03-07 papers/sbst22/data/utils.py

@@ -52,14 +52,23 @@ def save_fig(fig, filename):
     fig.savefig(filename, filetype='pdf', bbox_inches='tight', backend='pgf')
 
 
-def preload_latex_style():
+def preload_latex_style(document_class="ACM"):
     plt.style.use('seaborn')
     sns.set_style('whitegrid', {'grid.linewidth': 52})
     sns.set_context('paper')
-    load_custom_font = '\n'.join([
-        r'\usepackage{newtxtext,newtxmath}',
-        r'\usepackage[T1]{fontenc}',
-    ])
+
+    # Load custom fonts. ACM uses Linux Libertine, IEEE uses Times.
+    if document_class == "ACM":
+        load_custom_font = '\n'.join([
+            r'\usepackage{libertine,libertinust1math}',
+            r'\usepackage[T1]{fontenc}',
+        ])
+    elif document_class == "IEEE":
+        load_custom_font = '\n'.join([
+            r'\usepackage{}',
+            r'\usepackage[T1]{fontenc}',
+        ])
+
     plt.rcParams.update({
         'text.usetex': True,
         'pgf.texsystem': 'pdflatex',

### 2022-03-07 papers/sbst22/data/main.py
Also print benchmark names (for classes for which test gen failed)

@@ -139,8 +139,8 @@ utils.write_tex_macros('./macros.tex', utils.create_tex_macros(stats))
 
 
 def test_gen_failed_histogram(data):
-    return (test_gen_failed(data)[['class', 'testcaseNumber']]
-            .groupby('class')
+    return (test_gen_failed(data)[['benchmark', 'class', 'testcaseNumber']]
+            .groupby(['benchmark', 'class'])
             .count()
             .sort_values(by='testcaseNumber', ascending=False))
 

### 2022-03-10 papers/sbst22/paper_sbst22.tex
Switch to acmart
Add plots

@@
-%--------1---------2---------3---------4---------5---------6---------7
+\documentclass[sigconf,review,anonymous]{acmart}
 
-%\documentclass[10pt, conference, compsocconf]{IEEEtran}
-%\documentclass[10pt,conference,compsocconf]{IEEEtran}
-\documentclass[10pt,conference]{IEEEtran}
-
-%\documentclass[times, 10pt,twocolumn]{article} 
-%\usepackage{latex8}
-%\usepackage{times}
 \usepackage{amsfonts}
@@
 \usepackage{float}
-\usepackage[numbers,sort&compress,square]{natbib}
+%\usepackage[numbers,sort&compress,square]{natbib}
 \usepackage{graphicx}
 \usepackage{booktabs}
-\usepackage{subfigure}
+\usepackage{subcaption}
 %\usepackage{hyperref}
 \usepackage{color}
-\usepackage[usenames,dvipsnames,table]{xcolor}
+%\usepackage[usenames,dvipsnames,table]{xcolor}
 \usepackage{soul}
@@
 Andrea Arcuri\IEEEauthorrefmark{2},
-Jose Campos\IEEEauthorrefmark{3},
-and Annibale Panichella\IEEEauthorrefmark{4}%
+%Jose Campos\IEEEauthorrefmark{3},
+%and Annibale Panichella\IEEEauthorrefmark{4}%
 }
@@
 \IEEEauthorblockA{\IEEEauthorrefmark{1}University of Passau, Germany\\
-\{sebastian.vogl,sebastian.schweikl,gordon.fraser\}@uni-passau.de}
+\{sebastian.schweikl,gordon.fraser\}@uni-passau.de}
 \IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College and Oslo Metropolitan University, Norway\\andrea.arcuri@kristiania.no}
@@
 
-\maketitle
 %\thispagestyle{empty}
@@
 \end{abstract}
+
+\maketitle
 
@@
 
-\begin{figure}
+%\begin{figure}
+%  \centering
+%  \includegraphics[width=\columnwidth]{data/CoverageBoxV}
+%  \caption{Coverage results achieved in the competition.}
+%  \label{fig:results}
+%\end{figure}
+
+\begin{figure*}
   \centering
-	\includegraphics[width=\columnwidth]{data/CoverageBoxV}
-	\vspace{-2em}
-	\caption{\label{fig:results}Coverage results achieved in the competition.}
-	\vspace{-1em}
-\end{figure}
+  \begin{subfigure}{\columnwidth}
+    \includegraphics[width=\linewidth]{data/CoverageByBenchmark30.pdf}
+    \caption{Coverage results achieved in the competition with \SI{30}{\second}.}
+    \label{fig:results30}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{\columnwidth}
+    \includegraphics[width=\linewidth]{data/CoverageByBenchmark120.pdf}
+    \caption{Coverage results achieved in the competition with \SI{120}{\second}.}
+    \label{fig:results120}
+  \end{subfigure}
+
+  \caption{Creating subfigures in \LaTeX.}
+  \label{fig:figures}
+\end{figure*}
 

### 2022-03-13 papers/sbst22/paper_sbst22.tex
Add some text based on logs

@@
 %
-The annual unit test generation competition aims to drive and evaluate progress
-on unit test generation tools. Every year, a benchmark of Java classes is
-selected, and different test generation tools are evaluated in terms of the
-code coverage and mutation scores they can achieve on these classes. In the
-2022 edition of the competition, seven tools were applied on a set of \cuts classes.
-Details about the procedure of the competition, the technical framework, and
-the benchmark classes can be found in the competition report~\cite{SBST-toolcomp22}.
-\EVOSUITE achieved an overall score of \score, which was the highest among the
-competing and baseline tools.
+For the last 10 years, the annual unit test generation competition has
+evaluated progress on unit test generation tools using a benchmark of Java
+classes, on which different tools are applied and compared. In the 2022 edition
+of the competition, seven tools were applied on a set of \cuts classes. Details
+about the procedure of the competition, the technical framework, and the
+benchmark classes can be found in the competition
+report~\cite{SBST-toolcomp22}. \EVOSUITE achieved an overall score of \score,
+which was the highest among the competing and baseline tools.
 
@@
 
-\EVOSUITE~\cite{FrA11c} uses evolutionary search to automatically generate test
-suites for Java classes. It takes as input the name of a target class as well
-as the classpath describing where the compiled bytecode of the class as well as
-its dependencies are located. A basic static analysis extracts information
-about the relevant classes as well as their constructors, methods, and fields.
-The bytecode is instrumented while classes are loaded, such that \EVOSUITE can
-produce execution traces for test executions, and to avoid test flakiness by
-replacing non-deterministic calls with deterministic, mocked versions.
-\EVOSUITE then applies meta-heuristic search algorithms to automatically
-produce a set of JUnit test cases aimed at maximising code coverage.
+\EVOSUITE~\cite{FrA11c} automatically generates test suites for Java classes
+using evolutionary search. As input \EVOSUITE only requires the name of the
+target class as well as the classpath on which the compiled bytecode of the
+target class as well as its dependencies are located. \EVOSUITE first extracts
+information about the relevant classes as well as their constructors, methods,
+and fields using a basic static analysis. It instruments the bytecode while
+classes are loaded by the Java classloader, such that \EVOSUITE can produce
+execution traces for test executions, and to avoid test flakiness by replacing
+non-deterministic calls with deterministic, mocked versions. Finally, \EVOSUITE
+applies meta-heuristic search algorithms to automatically produce JUnit test
+cases aimed at maximising code coverage.
 %Besides the basic command line interface there are also plugins for popular development environments such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.
 
-Originally, \EVOSUITE was implemented to optimise entire test suites with
-respect to their overall code coverage~\cite{GoA_TSE12}.
-The latest search algorithm, which is now used by default, is the \textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search algorithm~\cite{dynamosa} which operates at the test case level.
+\EVOSUITE generates tests using evolutionary algorithms. 
 %
-The genetic encoding of test cases in \EVOSUITE consists of variable-length sequences of Java statements (e.g., primitive statements as well as calls on constructors or methods).
+For this, it uses a genetic encoding of test cases consisting of variable-length sequences of Java statements (e.g., primitive statements as well as calls on constructors or methods).
 Standard evolutionary search operators (e.g., selection, crossover, mutation) are adapted for this representation.
 %
-\EVOSUITE supports multiple different coverage criteria that can be optimised simultaneously.
-The core fitness functions in \EVOSUITE are based on traditional heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details).
-Further fitness functions are based on mutation testing~\cite{emse14_mutation} as well as other basic criteria~\cite{rojas2015combining}.
+\EVOSUITE provides several different evolutionary algorithms to operate on this
+representation. The initial approach was to optimise entire test suites with
+respect to their overall code coverage~\cite{GoA_TSE12}. However, after
+extensive evaluation~\cite{ea_evaluation} the default is now the
+\textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search
+algorithm~\cite{dynamosa}, which operates at the test case level.
+%
+The search is driven by fitness functions that encode coverage criteria.
+\EVOSUITE can optimise for several criteria simultaneously, and the core fitness functions in \EVOSUITE are based on traditional heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details).
+However, there are several further fitness functions based on mutation testing~\cite{emse14_mutation} as well as other basic criteria~\cite{rojas2015combining}.
 
-To improve the readability of the generated tests and to avoid test smells~\cite{panichella2020revisiting}, \EVOSUITE applies post-processing once the available search budget has been exhausted~\cite{FrA11c,FrA13a}.
-In particular, minimisation is used to remove redundant tests and statements, and a minimised set of assertions is added using mutation analysis~\cite{10.1109/TSE.2011.93}.
-Finally, \EVOSUITE compiles and executes each test individually to avoid compilation errors (which may be the result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the class under test.
+A large share of the complexity of \EVOSUITE's code base is due to efforts to
+avoid flakiness in the generated tests. One the one hand, this covers extensive
+instrumentation and mocking. On the other hand, \EVOSUITE also compiles and
+executes each test individually to avoid compilation errors (which may be the
+result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the
+class under test.
 
+\EVOSUITE is also heavily optimised in order to produce tests that are as readable as possible and avoid test smells~\cite{panichella2020revisiting}.
+For this, \EVOSUITE applies post-processing once the available search budget has been exhausted~\cite{FrA11c,FrA13a}, consisting of minimisation to remove redundant tests and statements, and adding a minimised set of assertions  using mutation analysis~\cite{10.1109/TSE.2011.93}.
 %Besides multiple in-depth empirical evaluations of \EVOSUITE with respect to
@@
 
-The most recent version of \EVOSUITE (1.1.0) was used in the competition. As of
-this version, the default search algorithm in \EVOSUITE is
-DynaMOSA~\cite{dynamosa}. No new features were added in this version, but
-support for Java 9+ was added, several bugs were fixed, and a major refactoring
-was applied to improve the code quality with respect to the use of Java
-generics internally. Several smaller bugfixes were applied in the run-up to the
-competition, which are now included in the current development version on
-GitHub.
+The 2022 competition setup was identical to the 2021 setup: The most recent
+version of \EVOSUITE (1.1.0) was used, which by default uses
+DynaMOSA~\cite{dynamosa} as the search algorithm. No new features were added in
+this version, but support for Java 9+ was added, several bugs were fixed, and a
+major refactoring was applied to improve the code quality with respect to the
+use of Java generics internally. While several smaller bugfixes were applied in
+the run-up to the 2021 competition, no further optimisation or testing was
+applied for 2022.
 
-The configuration of \EVOSUITE used in the 2021 competition is identical to the
-configuration used in prior years, and largely based on its tuned default
+The configuration is largely identical to the established configuration used in
+prior years, and mainly uses the tuned default
 values~\cite{arcuri2013parameter} and default coverage criteria
@@
 %
-Similar to prior competitions, the test minimisation step was omitted as the competition score does not reward test minimality, and the minimisation takes substantial computational effort.
-Similarly, we included all regression assertions rather than filtering them with mutation analysis to save time.
+As in previous years, the configuration omits the test minimisation step as the
+competition score does not reward test minimality, and the minimisation takes
+substantial computational effort. Similarly, the configuration includes all
+regression assertions rather than filtering them with mutation analysis to save
+time.
 %
-Same as in previous competitions, we allocated 50\% of
-the overall time set by the competition organisers for the search, and
-distributed the other 50\% equally to the remaining phases (e.g., assertion generation, compile-check, flakiness-check).
+The time budget was again distributed by allocating 50\% of the overall time
+set by the competition organisers for the search, and the other 50\% equally to
+the remaining phases (e.g., assertion generation, compile-check,
+flakiness-check).
 
@@
 for which all tools produced tests in some of the runs.
-Figure~\ref{fig:results} summarises the results of \EVOSUITE in terms of the
-mean coverage for the \cuts classes used in the competition. While the coverage
+Figure~\ref{fig:results30} summarises the results of \EVOSUITE in terms of the
+mean coverage for the \cuts classes used in the competition for the \budgetShort search budget; Figure~\ref{fig:results120} shows the results for the \budgetLong search budget. While the coverage
 increased from the \budgetShort to the \budgetLong search budget (mean line
@@
 the additional run of 300 seconds
-actually shows a slight decrease (mean line coverage of 73.9\%). The likely
-reason for this result is that \EVOSUITE crashed more frequently when given
-more time. For example, for 76 runs of \EVOSUITE on the \cuts classes no test
-cases were generated. In most cases we found that the JVM process running
-\EVOSUITE on the competition machine crashed with an
-\texttt{OutOfMemoryException}, which possibly could have been avoided with a
-more generous allocation of memory.
+actually shows a slight decrease (mean line coverage of 73.9\%). 
+%
+The likely reason for this result is that \EVOSUITE ran out of time more
+frequently when given more time. Indeed unlike past instances of the
+competition we found no crashes of \EVOSUITE (e.g., exceptions thrown by
+\EVOSUITE) at all, but in all cases where no tests were generated the \EVOSUITE
+process had been killed by the competition setup, suggesting that \EVOSUITE was
+using more time than allocated.
 
-The coverage ratios are generally higher than the mutation scores; while this is largely because it is simply more difficult to achieve a high mutation score, the mutation score is also negatively affected by classes with flakiness or failing tests (in which case the mutation score reported is 0\% by definition).
-Furthermore, in many cases the execution with the PIT mutation tool reported an error during class loading, which may be caused by configuration errors or clashes between \EVOSUITE's and PIT's bytecode instrumentation.
-
-A final observation is that all \cuts Java classes considered in the competition
-results were taken from the Guava project, which is notorious for its complex
-use of Java Generics---which is a feature \EVOSUITE still struggles to handle
-effectively. In particular, in 99 of all runs on the \cuts competition classes
-\EVOSUITE did not manage to move beyond the initial generation, which tends to
-happen specifically when \EVOSUITE struggles to correctly instantiate complex,
-nested generic types. This is currently a focus point of structural
-improvements and refactorings in \EVOSUITE's codebase.
+While the results for line coverage and branch coverage are similar, the
+mutation scores are substantially lower. The mutation scores on the Guava
+classes are highest compared to the other three projects from which classes
+were taken; this is surprising since Guava has been known for years to be
+notoriously challenging for
+\EVOSUITE~\cite{campos2015continuous,almulla2017using}. However, we find that
+in many cases the mutation analysis failed because dependency classes were
+missing on the classpath. While \EVOSUITE, JUnit and the coverage measurement
+used in the competition apparently were able to cope with this problem anyway,
+the PIT mutation analysis tool was unable to deal with this problem. This may
+likely be an error in the competition setup, but it would affect all test
+generation tools. While Spoon classes are affected the most, similar problems
+can be observed for all projects: Considering the \budgetLong runs we found
+\texttt{ClassNotFoundException}s in 414 runs for Spoon, 309 for Guava, 308 for
+Fastjson, and 329 for classes in Seata; in all these cases PIT was unable to
+run even when it was possible to measure coverage.
 
@@
 This paper reports on the participation of the \EVOSUITE test generation tool
-in the tenth SBST Java Unit Testing Tool Contest. On average, \EVOSUITE achieved
-\avgConditionsCoverageRatioLong branch coverage, \avgLinesCoverageRatioLong line coverage, 
-and a mutation score of \avgMutantsCoverageRatioLong, using a
-search budget of \budgetLong on the \cuts classes considered for the competition.
-Overall, this results in a score of \score, which is the highest score of all
-tools in the competition.
+in the tenth SBST Java Unit Testing Tool Contest. On average, \EVOSUITE
+achieved \avgConditionsCoverageRatioLong branch coverage,
+\avgLinesCoverageRatioLong line coverage, and a mutation score of
+\avgMutantsCoverageRatioLong, using a search budget of \budgetLong on the \cuts
+classes considered for the competition. Overall, this results in a score of
+\score, which is the highest score of all tools in the competition.
 
@@
 \EVOSUITE.
-This project has been supported by EPSRC project % ``GREATEST'' 
-EP/N023978/2.
+%This project has been supported by EPSRC project % ``GREATEST'' 
+%EP/N023978/2.
 

### 2022-03-13 papers/sbst22/paper_sbst22.tex
Fix format and authors, finish results

@@
-\documentclass[sigconf,review,anonymous]{acmart}
+%\documentclass[sigconf,review,anonymous]{acmart}
+\documentclass[sigconf]{acmart}
 
@@
 
-\author{%
-%
-\IEEEauthorblockN{%
-Sebastian Schweikl\IEEEauthorrefmark{1},
-Gordon Fraser\IEEEauthorrefmark{1}, 
-Andrea Arcuri\IEEEauthorrefmark{2},
-%Jose Campos\IEEEauthorrefmark{3},
-%and Annibale Panichella\IEEEauthorrefmark{4}%
+\author{Sebastian Schweikl}
+\affiliation{%
+  \institution{University of Passau}
+  \city{Passau}
+  \country{Germany}
 }
-%
-\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Passau, Germany\\
-\{sebastian.schweikl,gordon.fraser\}@uni-passau.de}
-\IEEEauthorblockA{\IEEEauthorrefmark{2}Kristiania University College and Oslo Metropolitan University, Norway\\andrea.arcuri@kristiania.no}
-\IEEEauthorblockA{\IEEEauthorrefmark{3}University of Lisbon, Portugal\\jcmcampos@fc.ul.pt}
-\IEEEauthorblockA{\IEEEauthorrefmark{4}Delft University of Technology, Netherlands\\A.Panichella@tudelft.nl}%
+%\email{gordon.fraser@uni-passau.de}
+
+\author{Gordon Fraser}
+\affiliation{%
+  \institution{University of Passau}
+  \city{Passau}
+  \country{Germany}
 }
+%\email{gordon.fraser@uni-passau.de}
 
+\author{Andrea Arcuri}
+\affiliation{%
+  \institution{Kristiania University College and Oslo Metropolitan University}
+  \city{Oslo}
+  \country{Norway}
+}
 %\thispagestyle{empty}
@@
 
-\begin{figure*}
+\begin{figure}
   \centering
-  \begin{subfigure}{\columnwidth}
+  \begin{subfigure}{0.9\columnwidth}
     \includegraphics[width=\linewidth]{data/CoverageByBenchmark30.pdf}
@@
   \hfill
-  \begin{subfigure}{\columnwidth}
+  \begin{subfigure}{0.9\columnwidth}
     \includegraphics[width=\linewidth]{data/CoverageByBenchmark120.pdf}
@@
 
-  \caption{Creating subfigures in \LaTeX.}
+  \caption{Competition results achieved by \EVOSUITE summarised by projects from which the classes under test.}
   \label{fig:figures}
-\end{figure*}
+\end{figure}
 
@@
 Figure~\ref{fig:results30} summarises the results of \EVOSUITE in terms of the
-mean coverage for the \cuts classes used in the competition for the \budgetShort search budget; Figure~\ref{fig:results120} shows the results for the \budgetLong search budget. While the coverage
+mean coverage for the \cuts classes used in the competition for the \budgetShort search budget; Figure~\ref{fig:results120} shows the results for the \budgetLong search budget. The coverage
 increased from the \budgetShort to the \budgetLong search budget (mean line
-coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively),
-the additional run of 300 seconds
-actually shows a slight decrease (mean line coverage of 73.9\%). 
-%
-The likely reason for this result is that \EVOSUITE ran out of time more
-frequently when given more time. Indeed unlike past instances of the
-competition we found no crashes of \EVOSUITE (e.g., exceptions thrown by
-\EVOSUITE) at all, but in all cases where no tests were generated the \EVOSUITE
-process had been killed by the competition setup, suggesting that \EVOSUITE was
-using more time than allocated.
+coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively).
+
+For \numTestGenFailedShort classes for \budgetShort, and \numTestGenFailedLong
+classes for \budgetLong, \EVOSUITE failed to generate any tests. Unlike past
+instances of the competition we found no crashes of \EVOSUITE (e.g., exceptions
+thrown by \EVOSUITE) at all, but in most cases where no tests were generated
+the \EVOSUITE process had been killed by the competition setup, suggesting that
+\EVOSUITE was using more time than allocated. In one class of the Seata project
+errors occurred during the initialisation of the target class, in which case
+\EVOSUITE simply gives up since the JVM does not allow instantiation of such
+classes.
 

### 2022-03-13 papers/sbst22/paper_sbst22.tex
Fix small typos

@@
 target class as well as the classpath on which the compiled bytecode of the
-target class as well as its dependencies are located. \EVOSUITE first extracts
+target class and its dependencies are located. \EVOSUITE first extracts
 information about the relevant classes as well as their constructors, methods,
@@
 extensive evaluation~\cite{ea_evaluation} the default is now the
-\textit{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search
+\emph{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search
 algorithm~\cite{dynamosa}, which operates at the test case level.
@@
 A large share of the complexity of \EVOSUITE's code base is due to efforts to
-avoid flakiness in the generated tests. One the one hand, this covers extensive
+avoid flakiness in the generated tests. On the one hand, this covers extensive
 instrumentation and mocking. On the other hand, \EVOSUITE also compiles and

### 2022-03-14 papers/sbst22/paper_sbst22.tex
Fix capitalisation

@@
 major refactoring was applied to improve the code quality with respect to the
-use of Java generics internally. While several smaller bugfixes were applied in
+use of Java Generics internally. While several smaller bugfixes were applied in
 the run-up to the 2021 competition, no further optimisation or testing was

### 2022-03-14 papers/sbst22/paper_sbst22.tex
Format project names with textsc

@@
 
+\newcommand{\project}[1]{\textsc{#1}}
+\newcommand{\Spoon}{\project{Spoon}}
+\newcommand{\Guava}{\project{Guava}}
+\newcommand{\Fastjson}{\project{Fastjson}}
+\newcommand{\Seata}{\project{Seata}}
 \newcommand{\JodaTime}{Joda-Time\xspace}  % That's how they write themselves -- AZ
@@
 the \EVOSUITE process had been killed by the competition setup, suggesting that
-\EVOSUITE was using more time than allocated. In one class of the Seata project
+\EVOSUITE was using more time than allocated. In one class of the \Seata project
 errors occurred during the initialisation of the target class, in which case
@@
 While the results for line coverage and branch coverage are similar, the
-mutation scores are substantially lower. The mutation scores on the Guava
+mutation scores are substantially lower. The mutation scores on the \Guava
 classes are highest compared to the other three projects from which classes
-were taken; this is surprising since Guava has been known for years to be
+were taken; this is surprising since \Guava has been known for years to be
 notoriously challenging for
@@
 likely be an error in the competition setup, but it would affect all test
-generation tools. While Spoon classes are affected the most, similar problems
+generation tools. While \Spoon classes are affected the most, similar problems
 can be observed for all projects: Considering the \budgetLong runs we found
-\texttt{ClassNotFoundException}s in 414 runs for Spoon, 309 for Guava, 308 for
-Fastjson, and 329 for classes in Seata; in all these cases PIT was unable to
+\texttt{ClassNotFoundException}s in 414 runs for \Spoon, 309 for \Guava, 308 for
+\Fastjson, and 329 for classes in \Seata; in all these cases PIT was unable to
 run even when it was possible to measure coverage.

### 2022-03-14 papers/sbst22/data/main.py
Update font style of projects in box plots
To make it consistent with the running text

@@ -61,7 +61,11 @@ data120 = all_data[budget(120)]
 
 
 def benchmark_basename(benchmark_name):
-    return benchmark_name.split('-')[0].capitalize()
+    return textsc(benchmark_name.split('-')[0].capitalize())
+
+
+def textsc(text):
+    return r'\textsc{' + text + '}'
 
 
 columns = {

### 2022-03-14 papers/sbst22/paper_sbst22.tex
Fix space issues with "project" macro
Use siunitx macros consistently

@@
 
-\newcommand{\project}[1]{\textsc{#1}}
+\newcommand{\project}[1]{\textsc{#1}\xspace}
 \newcommand{\Spoon}{\project{Spoon}}
@@
 %
-The time budget was again distributed by allocating 50\% of the overall time
-set by the competition organisers for the search, and the other 50\% equally to
+The time budget was again distributed by allocating \SI{50}{\percent} of the overall time
+set by the competition organisers for the search, and the other \SI{50}{\percent} equally to
 the remaining phases (e.g., assertion generation, compile-check,

### 2023-03-09 papers/sbst23/data/main.py
Add analysis scripts and raw analysis data

@@ -1,0 +1,166 @@
+#!/usr/bin/env python
+
+import pandas as pd
+import utils
+
+# The results.csv contains the raw evaluation results for 100 classes taken from 5 projects.
+# Two time budgets were used: 30s and 120s.
+all_data = pd.read_csv('./results.csv')
+
+# These are the columns in the CSV that contain coverage information.
+coverage_columns = ['linesCoverageRatio', 'conditionsCoverageRatio', 'mutantsCoverageRatio']
+
+# In the generated plots, we translate the original column names to more descriptive names.
+translation = ['Lines Covered', 'Branches Covered', 'Mutants Killed']
+
+# There's an additional column in the CSV that tells the time budget.
+# Here, we construct a dictionary with the four columns (three coverage related ones and the time budget) as key,
+# and their translation as value.
+columns = {
+    'timeBudget': 'Time Budget',
+    **dict(zip(coverage_columns, translation))
+}
+
+"""
+(1) Only keep the four columns we are interested in.
+(2) Rename the columns to give them more descriptive names.
+(3) Reshape the data such that the "Time Budget" is used as identifier, and the
+    remaining columns are "un-pivoted":
+
+          Time Budget          Metric     Percent
+    0              30   Lines Covered    0.000000
+    1              30   Lines Covered   20.833332
+    ...           ...             ...         ...
+    3898          120  Mutants Killed   55.882350
+    3899          120  Mutants Killed    0.000000
+"""
+plot_data = (all_data[columns.keys()]  # (1)
+             .rename(columns=columns)  # (2)
+             .melt(id_vars='Time Budget',
+                   var_name='Metric',
+                   value_name='Percent'))  # (3)
+
+"""
+Create a boxplot of the EvoSuite data per "Metric" on the x-axis, plotting the 
+corresponding values in the "Percent" column on the y-axis. Using "Time Budget"
+as hue key creates grouped a boxplot: for each metric, it actually plots two 
+boxes for the two budgets.
+"""
+utils.preload_latex_style("ACM")
+
+fig = utils.boxplot(data=plot_data,
+                    x='Metric',
+                    y='Percent',
+                    hue='Time Budget',
+                    title='Time Budget [s]',
+                    figsize=(3.5, 2.15))
+utils.save_fig(fig, './CoverageBoxV.pdf')
+
+
[…]

### 2023-03-09 papers/sbst23/data/utils.py

@@ -1,0 +1,112 @@
+import seaborn as sns
+import matplotlib.pyplot as plt
+
+
+def boxplot(data, x, y, hue, title=None, figsize=None):
+    if title is None:
+        title = hue
+
+    n_colors = data[hue].nunique()
+
+    def style_axes():
+        # Enlarge the range of the y-axis. Otherwise, whiskers at 0% or 100% are
+        # not visible.
+        ax.set_ylim(-5, 105)
+        all_axes = {'top': True, 'right': True, 'left': True, 'bottom': True}
+        sns.despine(fig, ax, **all_axes)
+
+    def set_legend():
+        # Remove the label from the x-axis. We create a separate "legend box"
+        # instead.
+        ax.set_xlabel('')
+        center_legend_below_plot = {
+            'loc': 'lower center',
+            'bbox_to_anchor': (0.5, -0.5)
+        }
+        ax.legend(title=title,
+                  ncol=n_colors,
+                  **center_legend_below_plot)
+
+    # Create a grouped boxplot using the supplied data. "x" is the column name
+    # of the data to plot on the x-axis, and "y" is the column name of the data
+    # to plot on the y-axis. The "hue" determines the subgroups.
+    fig = plt.figure(figsize=figsize)
+    palette = sns.color_palette(palette='pastel', n_colors=n_colors)
+    flierprops = {'marker': 'o', 'markersize': 1.0}
+    ax = sns.boxplot(data=data, x=x, y=y, hue=hue, palette=palette,
+                     linewidth=0.5, flierprops=flierprops)
+
+    style_axes()
+
+    # Display a legend below the plot, also giving the x-axis a label
+    # (or "title"). The main purpose of the legend is to distinguish the boxes
+    # within a grouped boxplot via their color.
+    set_legend()
+
+    return fig
+
+
+def save_fig(fig, filename):
+    # Save the plot as a PDF. Without bbox_inches='tight', the legend is missing
+    # in the PDF...
+    fig.savefig(filename, bbox_inches='tight', backend='pgf')
+
+
+def preload_latex_style(document_class="ACM"):
+    plt.style.use('seaborn')
+    sns.set_style('whitegrid', {'grid.linewidth': 52})
+    sns.set_context('paper')
+
+    # Load custom fonts. ACM uses Linux Libertine, IEEE uses Times.
+    if document_class == "ACM":
+        load_custom_font = '\n'.join([
[…]

### 2023-03-09 papers/sbst23/data/main.py
fine tune box plot caption

@@ -70,7 +70,8 @@ data120 = all_data[budget(120)]
 # respectively.
 def benchmark_basename(benchmark_name):
     sep = '-'
-    basename = sep.join(benchmark_name.split(sep)[0:-1])  # drop the number at the end
+    # basename = sep.join(benchmark_name.split(sep)[0:-1])  # drop the number at the end
+    basename = benchmark_name.split(sep)[0]
     return textsc(basename.capitalize())
 
 

### 2023-03-09 papers/sbst23/data/utils.py

@@ -21,10 +21,10 @@ def boxplot(data, x, y, hue, title=None, figsize=None):
         ax.set_xlabel('')
         center_legend_below_plot = {
             'loc': 'lower center',
-            'bbox_to_anchor': (0.5, -0.5)
+            'bbox_to_anchor': (0.5, -0.6)
         }
         ax.legend(title=title,
-                  ncol=n_colors,
+                  ncol=min(3, n_colors),
                   **center_legend_below_plot)
 
     # Create a grouped boxplot using the supplied data. "x" is the column name

### 2023-03-09 papers/sbst23/data/main.py
WIP: try to create stacked subplots

@@ -1,5 +1,6 @@
 #!/usr/bin/env python
 
+import matplotlib.pyplot as plt
 import pandas as pd
 import utils
 
@@ -48,12 +49,13 @@ boxes for the two budgets.
 """
 utils.preload_latex_style("ACM")
 
-fig = utils.boxplot(data=plot_data,
-                    x='Metric',
-                    y='Percent',
-                    hue='Time Budget',
-                    title='Time Budget [s]',
-                    figsize=(3.5, 2.15))
+fig = plt.figure(figsize=(3.5, 2.15))
+ax = utils.boxplot(data=plot_data,
+                   x='Metric',
+                   y='Percent',
+                   hue='Time Budget')
+utils.style_axes(fig, ax)
+utils.set_legend(ax, title="Time Budget [s]", ncol=2)
 utils.save_fig(fig, './CoverageBoxV.pdf')
 
 
@@ -92,13 +94,6 @@ data_by_benchmark30 = (data30[['benchmark', *coverage_columns]]
 benchmarks = data_by_benchmark30['Benchmark'].copy()
 data_by_benchmark30['Benchmark'] = benchmarks.map(benchmark_basename)
 
-fig = utils.boxplot(data=data_by_benchmark30,
-                    x='Metric',
-                    y='Percent',
-                    hue='Benchmark',
-                    figsize=(3.5, 2.15))
-utils.save_fig(fig, './CoverageByBenchmark30.pdf')
-
 data_by_benchmark120 = (data120[['benchmark', *coverage_columns]]
                         .rename(columns=columns)
                         .melt(id_vars='Benchmark',
@@ -107,12 +102,38 @@ data_by_benchmark120 = (data120[['benchmark', *coverage_columns]]
 benchmarks = data_by_benchmark120['Benchmark'].copy()
 data_by_benchmark120['Benchmark'] = benchmarks.map(benchmark_basename)
 
-fig = utils.boxplot(data=data_by_benchmark120,
-                    x='Metric',
-                    y='Percent',
-                    hue='Benchmark',
-                    figsize=(3.5, 2.15))
+fig = plt.figure(figsize=(3.5, 2.15))
+ax = utils.boxplot(data=data_by_benchmark30,
+                   x='Metric',
+                   y='Percent',
+                   hue='Benchmark')
+utils.style_axes(fig, ax)
+utils.set_legend(ax, title='', ncol=3)
[…]

### 2023-03-09 papers/sbst23/data/utils.py

@@ -2,48 +2,44 @@ import seaborn as sns
 import matplotlib.pyplot as plt
 
 
-def boxplot(data, x, y, hue, title=None, figsize=None):
-    if title is None:
-        title = hue
-
+def boxplot(data, *, x, y, hue, ax=None):
     n_colors = data[hue].nunique()
-
-    def style_axes():
-        # Enlarge the range of the y-axis. Otherwise, whiskers at 0% or 100% are
-        # not visible.
-        ax.set_ylim(-5, 105)
-        all_axes = {'top': True, 'right': True, 'left': True, 'bottom': True}
-        sns.despine(fig, ax, **all_axes)
-
-    def set_legend():
-        # Remove the label from the x-axis. We create a separate "legend box"
-        # instead.
-        ax.set_xlabel('')
-        center_legend_below_plot = {
-            'loc': 'lower center',
-            'bbox_to_anchor': (0.5, -0.6)
-        }
-        ax.legend(title=title,
-                  ncol=min(3, n_colors),
-                  **center_legend_below_plot)
 
     # Create a grouped boxplot using the supplied data. "x" is the column name
     # of the data to plot on the x-axis, and "y" is the column name of the data
     # to plot on the y-axis. The "hue" determines the subgroups.
-    fig = plt.figure(figsize=figsize)
     palette = sns.color_palette(palette='pastel', n_colors=n_colors)
     flierprops = {'marker': 'o', 'markersize': 1.0}
-    ax = sns.boxplot(data=data, x=x, y=y, hue=hue, palette=palette,
-                     linewidth=0.5, flierprops=flierprops)
 
-    style_axes()
+    if ax is None:
+        ax = sns.boxplot(data=data, x=x, y=y, hue=hue, palette=palette,
+                         linewidth=0.5, flierprops=flierprops)
+    else:
+        sns.boxplot(data=data, x=x, y=y, hue=hue, palette=palette,
+                    linewidth=0.5, flierprops=flierprops, ax=ax)
 
-    # Display a legend below the plot, also giving the x-axis a label
-    # (or "title"). The main purpose of the legend is to distinguish the boxes
-    # within a grouped boxplot via their color.
-    set_legend()
+    return ax
 
-    return fig
+
+def style_axes(fig, ax):
+    # Enlarge the range of the y-axis. Otherwise, whiskers at 0% or 100% are
+    # not visible.
+    ax.set_ylim(-5, 105)
[…]

### 2023-03-10 papers/sbst23/data/main.py
Plot, data: human study, understandability

@@ -54,7 +54,7 @@ ax = utils.boxplot(data=plot_data,
                    x='Metric',
                    y='Percent',
                    hue='Time Budget')
-utils.style_axes(fig, ax)
+utils.style_axes(fig, ax, ylim=(-5, 105))
 utils.set_legend(ax, title="Time Budget [s]", ncol=2)
 utils.save_fig(fig, './CoverageBoxV.pdf')
 
@@ -74,11 +74,7 @@ def benchmark_basename(benchmark_name):
     sep = '-'
     # basename = sep.join(benchmark_name.split(sep)[0:-1])  # drop the number at the end
     basename = benchmark_name.split(sep)[0]
-    return textsc(basename.capitalize())
-
-
-def textsc(text):
-    return r'\textsc{' + text + '}'
+    return utils.textsc(basename.capitalize())
 
 
 columns = {
@@ -107,7 +103,7 @@ ax = utils.boxplot(data=data_by_benchmark30,
                    x='Metric',
                    y='Percent',
                    hue='Benchmark')
-utils.style_axes(fig, ax)
+utils.style_axes(fig, ax, ylim=(-5, 105))
 utils.set_legend(ax, title='', ncol=3)
 utils.save_fig(fig, './CoverageByBenchmark30.pdf')
 
@@ -116,7 +112,7 @@ ax = utils.boxplot(data=data_by_benchmark120,
               x='Metric',
               y='Percent',
               hue='Benchmark')
-utils.style_axes(fig, ax)
+utils.style_axes(fig, ax, ylim=(-5, 105))
 utils.set_legend(ax, title='', ncol=3)
 utils.save_fig(fig, './CoverageByBenchmark120.pdf')
 

### 2023-03-10 papers/sbst23/data/understandability.py

@@ -1,0 +1,20 @@
+import pandas as pd
+import matplotlib.pyplot as plt
+import utils
+
+utils.preload_latex_style("ACM")
+
+data = pd.read_csv('./human-study.csv')
+
+columns = [q + '_EV' for q in ['Q2', 'Q6', 'Q9']]
+tool_names = ['Collections', 'Threeten', 'Spatial4j']
+
+data_EV = data[columns].rename(columns={key: utils.textsc(value) for key, value in zip(columns, tool_names)})
+
+fig = plt.figure(figsize=(3.5, 2.15))
+ax = utils.violinplot(data_EV)
+ax.set_yticks(range(1, 6))
+utils.style_axes(fig, ax)
+ax.set_ylabel('Understandability Rank')
+
+utils.save_fig(fig, './understandability.pdf')

### 2023-03-10 papers/sbst23/data/utils.py

@@ -2,8 +2,8 @@ import seaborn as sns
 import matplotlib.pyplot as plt
 
 
-def boxplot(data, *, x, y, hue, ax=None):
-    n_colors = data[hue].nunique()
+def boxplot(data, *, x=None, y=None, hue=None, ax=None):
+    n_colors = 1 if hue is None else data[hue].nunique()
 
     # Create a grouped boxplot using the supplied data. "x" is the column name
     # of the data to plot on the x-axis, and "y" is the column name of the data
@@ -21,10 +21,32 @@ def boxplot(data, *, x, y, hue, ax=None):
     return ax
 
 
-def style_axes(fig, ax):
+def violinplot(data, *, x=None, y=None, hue=None, ax=None):
+    n_colors = 1 if hue is None else data[hue].nunique()
+
+    # Create a grouped boxplot using the supplied data. "x" is the column name
+    # of the data to plot on the x-axis, and "y" is the column name of the data
+    # to plot on the y-axis. The "hue" determines the subgroups.
+    palette = sns.color_palette(palette='pastel', n_colors=n_colors)
+    flierprops = {'marker': 'o', 'markersize': 1.0}
+
+    if ax is None:
+        ax = sns.violinplot(data=data, x=x, y=y, hue=hue, palette=palette,
+                            linewidth=0.5, flierprops=flierprops)
+    else:
+        sns.violinplot(data=data, x=x, y=y, hue=hue, palette=palette,
+                       linewidth=0.5, flierprops=flierprops, ax=ax)
+
+    return ax
+
+
+def style_axes(fig, ax, ylim=None):
     # Enlarge the range of the y-axis. Otherwise, whiskers at 0% or 100% are
     # not visible.
-    ax.set_ylim(-5, 105)
+    if ylim is not None:
+        ylim_x, ylim_y = ylim
+        ax.set_ylim(ylim_x, ylim_y)
+
     all_axes = {'top': True, 'right': True, 'left': True, 'bottom': True}
     sns.despine(fig, ax, **all_axes)
 
@@ -106,3 +128,6 @@ def write_tex_macros(filename, macros):
     with open(filename, 'w') as f:
         lines = '\n'.join(macros)
         f.write(lines)
+
+def textsc(text):
+    return r'\textsc{' + text + '}'

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Update numbers

--- 2022-03-14 papers/sbst22/paper_sbst22.tex
@@
 
+\copyrightyear{2022}
+\acmYear{2022}
+\setcopyright{acmcopyright}
+\acmConference[SBST'22 ]{The 15th Search-Based Software Testing Workshop}{May 9, 2022}{Pittsburgh, PA, USA}
+\acmBooktitle{The 15th Search-Based Software Testing Workshop (SBST'22 ), May 9, 2022, Pittsburgh, PA, USA}
+\acmPrice{15.00}
+\acmDOI{10.1145/3526072.3527526}
+\acmISBN{978-1-4503-9318-8/22/05}
+
 %-------------------------------------------------------------------------
 % take the % away on next line to produce the final camera-ready version
-%\pagestyle{empty}
+\pagestyle{empty}
 
@@
 %\title{Unit Testing Tool competition: Results for EvoSuite}
-\title{\EVOSUITE at the SBST 2022 Tool Competition}
+\title{\EVOSUITE at the SBFT 2023 Tool Competition}
 
@@
   \EVOSUITE is a search-based unit test generation tool for Java.
-This paper summarises the results and experiences of \EVOSUITE's participation at the 10th unit testing competition at SBST 2022, where \EVOSUITE achieved the highest overall score.
+This paper summarises the results and experiences of \EVOSUITE's participation at the 11th unit testing competition at SBFT 2023, where \EVOSUITE achieved the highest overall score.
 \end{abstract}
@@
 evaluated progress on unit test generation tools using a benchmark of Java
-classes, on which different tools are applied and compared. In the 2022 edition
-of the competition, seven tools were applied on a set of \cuts classes. Details
+classes, on which different tools are applied and compared. In the 2023 edition
+of the competition, five tools were applied on a set of \cuts classes. Details
 about the procedure of the competition, the technical framework, and the

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Results for test case readability

@@
 \newcommand{\project}[1]{\textsc{#1}\xspace}
-\newcommand{\Spoon}{\project{Spoon}}
-\newcommand{\Guava}{\project{Guava}}
-\newcommand{\Fastjson}{\project{Fastjson}}
-\newcommand{\Seata}{\project{Seata}}
-\newcommand{\JodaTime}{Joda-Time\xspace}  % That's how they write themselves -- AZ
+\newcommand{\Collections}{\project{Collections}}
+\newcommand{\Threeten}{\project{Threeten}}
+\newcommand{\Spatial}{\project{Spatial4j}}
 
@@
 
+For the first time, the competition also assessed test case readability. To this,
+a human study with 13 participants was conducted. A random class under test
+was selected per the \Collections, \Threeten, and \Spatial projects, for which
+every competing tool generated one test case. Then, each participant was asked
+to rank these test cases on a scale from 1 (best) to 5 (worst), in terms of
+readability. Overall, \EVOSUITE achieved the 2nd highest rank. The rank
+distribution is shown in Figure~\ref{fig:readability}.
+
+Most participants found \EVOSUITE-generated tests to be readable. When
+\EVOSUITE ranked highest, they positively highlighted the thoroughness of
+generated assertions, using edge cases as inputs, and the fact that tests
+where short. When \EVOSUITE ranked lowest, participants critized the lack
+of comments and descriptive test names, repetitiveness in the code, and
+needless assertions.
+
+\EVOSUITE's test case for \Collections was the longest among all presented
+ones. Interestingly, it ranked both highest and lowest, with participants
+stating that it was ``the most complete'' and the code being ``longer making
+it more confusing''.
+
+\begin{figure}
+  \includegraphics[width=0.9\columnwidth]{./data/understandability}
+  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project.}
+  \label{fig:readability}
+\end{figure}
+
 %-------------------------------------------------------------------------

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Fix compile errors

@@
 the \EVOSUITE process had been killed by the competition setup, suggesting that
-\EVOSUITE was using more time than allocated. In one class of the \Seata project
+\EVOSUITE was using more time than allocated. In one class of the FIXME project
 errors occurred during the initialisation of the target class, in which case
@@
 While the results for line coverage and branch coverage are similar, the
-mutation scores are substantially lower. The mutation scores on the \Guava
+mutation scores are substantially lower. The mutation scores on the FIXME
 classes are highest compared to the other three projects from which classes
-were taken; this is surprising since \Guava has been known for years to be
+were taken; this is surprising since FIXME has been known for years to be
 notoriously challenging for
@@
 likely be an error in the competition setup, but it would affect all test
-generation tools. While \Spoon classes are affected the most, similar problems
+generation tools. While FIXME classes are affected the most, similar problems
 can be observed for all projects: Considering the \budgetLong runs we found
-\texttt{ClassNotFoundException}s in 414 runs for \Spoon, 309 for \Guava, 308 for
-\Fastjson, and 329 for classes in \Seata; in all these cases PIT was unable to
+\texttt{ClassNotFoundException}s in 414 runs for FIXME, 309 for FIXME, 308 for
+FIXME, and 329 for classes in FIXME; in all these cases PIT was unable to
 run even when it was possible to measure coverage.

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Update some results

--- 2023-03-10 papers/sbst23/paper_sbst23.tex
@@
   \centering
+
   \begin{subfigure}{0.9\columnwidth}
@@
   \end{subfigure}
-  \hfill
+
   \begin{subfigure}{0.9\columnwidth}
@@
 tools in the competition. As described in the competition
-report~\cite{SBST-toolcomp22}, the score is calculated on the subset of \cuts classes
-for which all tools produced tests in some of the runs.
+report~\cite{SBST-toolcomp22}, the score is the weighted sum between the
+rankings for coverage and understandability.
+
 Figure~\ref{fig:results30} summarises the results of \EVOSUITE in terms of the
@@
 
-For \numTestGenFailedShort classes for \budgetShort, and \numTestGenFailedLong
-classes for \budgetLong, \EVOSUITE failed to generate any tests. Unlike past
-instances of the competition we found no crashes of \EVOSUITE (e.g., exceptions
-thrown by \EVOSUITE) at all, but in most cases where no tests were generated
-the \EVOSUITE process had been killed by the competition setup, suggesting that
-\EVOSUITE was using more time than allocated. In one class of the \Seata project
-errors occurred during the initialisation of the target class, in which case
-\EVOSUITE simply gives up since the JVM does not allow instantiation of such
-classes.
+\EVOSUITE failed to generate any tests in \numTestGenFailedShort cases with a
+budget of \budgetShort, and in \numTestGenFailedLong cases with a budget of
+\budgetLong. However, we found no crashes of \EVOSUITE itself (e.g., exceptions
+thrown by \EVOSUITE), but in all cases where no tests were generated the
+\EVOSUITE process had been killed by the competition setup, suggesting that
+\EVOSUITE was using more time than allocated.
 
 While the results for line coverage and branch coverage are similar, the
-mutation scores are substantially lower. The mutation scores on the \Guava
-classes are highest compared to the other three projects from which classes
-were taken; this is surprising since \Guava has been known for years to be
-notoriously challenging for
-\EVOSUITE~\cite{campos2015continuous,almulla2017using}. However, we find that
-in many cases the mutation analysis failed because dependency classes were
-missing on the classpath. While \EVOSUITE, JUnit and the coverage measurement
-used in the competition apparently were able to cope with this problem anyway,
-the PIT mutation analysis tool was unable to deal with this problem. This may
-likely be an error in the competition setup, but it would affect all test
-generation tools. While \Spoon classes are affected the most, similar problems
-can be observed for all projects: Considering the \budgetLong runs we found
-\texttt{ClassNotFoundException}s in 414 runs for \Spoon, 309 for \Guava, 308 for
-\Fastjson, and 329 for classes in \Seata; in all these cases PIT was unable to
-run even when it was possible to measure coverage.
+mutation scores are substantially lower. The mutation scores on the \Threeten
+classes are highest compared to the other projects from which classes were taken.
+
+For the first time, the competition also conducted a human study with 13
+participants to assess test case readability. To this, a method under test
+was chosen for each of the \Collections, \Threeten, and \Spatial
+projects. Then, for each competitor a test covering that method was selected
+randomly among the generated ones. Finally, the participants were asked
+to rank the tests for each project on a scale from 1 (best) to 5 (worst),
+in terms of readability. Overall, \EVOSUITE achieved the 2nd highest rank
+rating. Its distribution is shown in Figure~\ref{fig:readability}.
+
+Most participants found \EVOSUITE-generated tests to be readable. When
+\EVOSUITE ranked highest, they positively highlighted the thoroughness of
+generated assertions, using edge cases as inputs, and the fact that tests
+where short. When \EVOSUITE ranked lowest, participants criticised the lack
+of comments and descriptive test names, repetitiveness in the code, and
+needless assertions.
+
+Among the tests for \Collections the longest one was produced by \EVOSUITE.
+Interestingly, it ranked both highest and lowest, with one participant
+stating it was ``the most complete'', while another suggested the code
+being longer makes it ``more confusing''.
+
+\begin{figure}
+  \includegraphics[width=0.9\columnwidth]{./data/understandability}
+  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project.}
+  \label{fig:readability}
+\end{figure}
 

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Small pass over competition setup

@@
 
-The 2022 competition setup was identical to the 2021 setup: The most recent
-version of \EVOSUITE (1.1.0) was used, which by default uses
-DynaMOSA~\cite{dynamosa} as the search algorithm. No new features were added in
-this version, but support for Java 9+ was added, several bugs were fixed, and a
-major refactoring was applied to improve the code quality with respect to the
-use of Java Generics internally. While several smaller bugfixes were applied in
-the run-up to the 2021 competition, no further optimisation or testing was
-applied for 2022.
+The 2023 competition setup was similar to the 2022 setup: The same version of
+\EVOSUITE (1.1.0) was used, which by default uses DynaMOSA~\cite{dynamosa} as
+the search algorithm.
+% No new features were added in this version, but support
+% for Java 9+ was added, several bugs were fixed, and amajor refactoring was applied
+% to improve the code quality with respect to the
+% use of Java Generics internally. While several smaller bugfixes were applied in
+% the run-up to the 2021 competition, no further optimisation or testing was
+% applied for 2022.
 
@@
 %
-As in previous years, the configuration omits the test minimisation step as the
-competition score does not reward test minimality, and the minimisation takes
-substantial computational effort. Similarly, the configuration includes all
-regression assertions rather than filtering them with mutation analysis to save
-time.
+Unlike previous years, where the competition score did not yet reward readability,
+the configuration now enables a test minimisation step, and filters regression
+assertions using mutation analysis.
 %
@@
 set by the competition organisers for the search, and the other \SI{50}{\percent} equally to
-the remaining phases (e.g., assertion generation, compile-check,
-flakiness-check).
+the remaining phases (e.g., assertion generation, compile-check, flakiness-check).
 

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Pass over readability results

@@
 \newcommand{\EVOSUITE}{\textsc{EvoSuite}\xspace}
-\newcommand{\JTEXPERT}{\textsc{jTExpert}\xspace}
-\newcommand{\RANDOOP}{\textsc{Randoop}\xspace}
+\newcommand{\UtbotConcolic}{\textsc{Utbot-concolic}\xspace}
 \newcommand{\TT}{\textsc{T3}\xspace}
@@
 For the first time, the competition also conducted a human study with 13
-participants to assess test case readability. To this, a method under test
-was chosen for each of the \Collections, \Threeten, and \Spatial
-projects. Then, for each competitor a test covering that method was selected
-randomly among the generated ones. Finally, the participants were asked
-to rank the tests for each project on a scale from 1 (best) to 5 (worst),
-in terms of readability. Overall, \EVOSUITE achieved the 2nd highest rank
-rating. Its distribution is shown in Figure~\ref{fig:readability}.
+participants to assess test case readability. For each of the projects \Collections,
+\Threeten, and \Spatial, participants were presented a test case
+generated by each of the six competing tools, covering the same method under
+test. The participants were then asked to rank the tests per project
+on a scale from 1 (best) to 5 (worst), in terms of readability. Overall,
+\EVOSUITE achieved the 2nd best rating (rank 2.23 on average), only
+preceded by \UtbotConcolic (2.13 on average). \EVOSUITE's rank distribution
+is shown in Figure~\ref{fig:readability}.
 
 Most participants found \EVOSUITE-generated tests to be readable. When
-\EVOSUITE ranked highest, they positively highlighted the thoroughness of
+\EVOSUITE ranked best, they positively highlighted the thoroughness of
 generated assertions, using edge cases as inputs, and the fact that tests
-where short. When \EVOSUITE ranked lowest, participants criticised the lack
+where short. When \EVOSUITE ranked worst, participants criticised the lack
 of comments and descriptive test names, repetitiveness in the code, and
-needless assertions.
+needless assertions. While \EVOSUITE's competition setup enabled test and
+assertion minimisation, this is a computationally very expensive process,
+and it is likely \EVOSUITE was sometimes unable to finish in time,
+leaving tests unoptimised.
 

### 2023-03-10 papers/sbst23/paper_sbst23.tex
Switch from acmart to IEEEtran

@@
-%\documentclass[sigconf,review,anonymous]{acmart}
-\documentclass[sigconf]{acmart}
+\documentclass[10pt,conference]{IEEEtran}
 
@@
 
-\copyrightyear{2022}
-\acmYear{2022}
-\setcopyright{acmcopyright}
-\acmConference[SBST'22 ]{The 15th Search-Based Software Testing Workshop}{May 9, 2022}{Pittsburgh, PA, USA}
-\acmBooktitle{The 15th Search-Based Software Testing Workshop (SBST'22 ), May 9, 2022, Pittsburgh, PA, USA}
-\acmPrice{15.00}
-\acmDOI{10.1145/3526072.3527526}
-\acmISBN{978-1-4503-9318-8/22/05}
-
 %-------------------------------------------------------------------------
@@
 
-\author{Sebastian Schweikl}
-\affiliation{%
-  \institution{University of Passau}
-  \city{Passau}
-  \country{Germany}
+\author{%
+  \IEEEauthorblockN{Sebastian Schweikl}
+  \IEEEauthorblockA{%
+    \textit{University of Passau} \\
+    Passau, Germany \\
+    email address or ORCID
   }
-%\email{gordon.fraser@uni-passau.de}
+  \and
+  \IEEEauthorblockN{Gordon Fraser}
+  \IEEEauthorblockA{%
+    \textit{University of Passau} \\
+    Passau, Germany \\
+    email address or ORCID
+  }
+  \and
+  \IEEEauthorblockN{Andrea Arcur}
+  \IEEEauthorblockA{%
+    \textit{Kristiania University College and Oslo Metropolitan University} \\
+    Oslo, Norway \\
+    email address or ORCID
+  }
+}
 
-\author{Gordon Fraser}
-\affiliation{%
-  \institution{University of Passau}
-  \city{Passau}
-  \country{Germany}
-}
-%\email{gordon.fraser@uni-passau.de}
-
-\author{Andrea Arcuri}
-\affiliation{%
-  \institution{Kristiania University College and Oslo Metropolitan University}
-  \city{Oslo}
-  \country{Norway}
-}
-%\thispagestyle{empty}
+\maketitle
 
@@
 \end{abstract}
-
-\maketitle
 

### 2023-03-10 papers/sbst23/data/main.py
Update and regenerate graphics

@@ -12,7 +12,7 @@ all_data = pd.read_csv('./results.csv')
 coverage_columns = ['linesCoverageRatio', 'conditionsCoverageRatio', 'mutantsCoverageRatio']
 
 # In the generated plots, we translate the original column names to more descriptive names.
-translation = ['Lines Covered', 'Branches Covered', 'Mutants Killed']
+translation = ['Lines', 'Branches', 'Mutants']
 
 # There's an additional column in the CSV that tells the time budget.
 # Here, we construct a dictionary with the four columns (three coverage related ones and the time budget) as key,
@@ -47,7 +47,7 @@ corresponding values in the "Percent" column on the y-axis. Using "Time Budget"
 as hue key creates grouped a boxplot: for each metric, it actually plots two 
 boxes for the two budgets.
 """
-utils.preload_latex_style("ACM")
+utils.preload_latex_style("IEEE")
 
 fig = plt.figure(figsize=(3.5, 2.15))
 ax = utils.boxplot(data=plot_data,
@@ -56,6 +56,7 @@ ax = utils.boxplot(data=plot_data,
                    hue='Time Budget')
 utils.style_axes(fig, ax, ylim=(-5, 105))
 utils.set_legend(ax, title="Time Budget [s]", ncol=2)
+ax.set_ylabel('Coverage [%]')
 utils.save_fig(fig, './CoverageBoxV.pdf')
 
 
@@ -105,6 +106,7 @@ ax = utils.boxplot(data=data_by_benchmark30,
                    hue='Benchmark')
 utils.style_axes(fig, ax, ylim=(-5, 105))
 utils.set_legend(ax, title='', ncol=3)
+ax.set_ylabel('Coverage [%]')
 utils.save_fig(fig, './CoverageByBenchmark30.pdf')
 
 fig = plt.figure(figsize=(3.5, 2.15))
@@ -114,6 +116,7 @@ ax = utils.boxplot(data=data_by_benchmark120,
               hue='Benchmark')
 utils.style_axes(fig, ax, ylim=(-5, 105))
 utils.set_legend(ax, title='', ncol=3)
+ax.set_ylabel('Coverage [%]')
 utils.save_fig(fig, './CoverageByBenchmark120.pdf')
 
 # fig, (ax1, ax2) = plt.subplots(1, 2, figsize=(7, 2.15), sharey=True)

### 2023-03-10 papers/sbst23/data/understandability.py

@@ -2,7 +2,7 @@ import pandas as pd
 import matplotlib.pyplot as plt
 import utils
 
-utils.preload_latex_style("ACM")
+utils.preload_latex_style("IEEE")
 
 data = pd.read_csv('./human-study.csv')
 

### 2023-03-10 papers/sbst23/data/utils.py

@@ -83,7 +83,7 @@ def preload_latex_style(document_class="ACM"):
         ])
     elif document_class == "IEEE":
         load_custom_font = '\n'.join([
-            r'\usepackage{}',
+            r'\usepackage{newtxtext,newtxmath}',
             r'\usepackage[T1]{fontenc}',
         ])
     elif document_class == "beamer":

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Fine tune figures
Fix typo
Format long affiliation
WIP: results

@@
   \and
-  \IEEEauthorblockN{Andrea Arcur}
+  \IEEEauthorblockN{Andrea Arcuri}
   \IEEEauthorblockA{%
-    \textit{Kristiania University College and Oslo Metropolitan University} \\
+    \textit{Kristiania University College and}\\ \textit{Oslo Metropolitan University} \\
     Oslo, Norway \\
@@
 benchmark classes can be found in the competition
-report~\cite{SBST-toolcomp22}. \EVOSUITE achieved an overall score of \score,
+report~\cite{SBFT-toolcomp23}. \EVOSUITE achieved an overall score of \score,
 which was the highest among the competing and baseline tools.
@@
 %-------------------------------------------------------------------------
-\section{Competition Setup}
+\section{Competition Setup}\label{sec:setup}
 
@@
 
-  \begin{subfigure}{0.9\columnwidth}
+  \begin{subfigure}{\columnwidth}
     \includegraphics[width=\linewidth]{data/CoverageByBenchmark30.pdf}
-    \caption{Coverage results achieved in the competition with \SI{30}{\second}.}
+    \caption{Results achieved in the competition with a budget of \budgetShort}
     \label{fig:results30}
@@
 
-  \begin{subfigure}{0.9\columnwidth}
+  \begin{subfigure}{\columnwidth}
     \includegraphics[width=\linewidth]{data/CoverageByBenchmark120.pdf}
-    \caption{Coverage results achieved in the competition with \SI{120}{\second}.}
+    \caption{Results achieved in the competition with a budget of \budgetLong}
     \label{fig:results120}
@@
 
-  \caption{Competition results achieved by \EVOSUITE summarised by projects from which the classes under test.}
+  \caption{Coverage results achieved by \EVOSUITE per each of the 5~projects
+    used in the competition}
   \label{fig:figures}
@@
 
-With an overall score of \score, \EVOSUITE achieved the highest score of all
-tools in the competition. As described in the competition
-report~\cite{SBST-toolcomp22}, the score is the weighted sum between the
-rankings for coverage and understandability.
+With an overall score of \score \EVOSUITE was the highest ranking tool
+(rank \rank) in the competition. The score is computed as the weighted
+sum between the rankings for coverage (rank \rankCoverage) and understandability
+(rank \rankUnderstandability). We refer to the competition report~\cite{SBFT-toolcomp23}
+for more details.
 
-Figure~\ref{fig:results30} summarises the results of \EVOSUITE in terms of the
-mean coverage for the \cuts classes used in the competition for the \budgetShort search budget; Figure~\ref{fig:results120} shows the results for the \budgetLong search budget. The coverage
-increased from the \budgetShort to the \budgetLong search budget (mean line
-coverage of \avgLinesCoverageRatioShort vs. \avgLinesCoverageRatioLong, respectively).
+The coverage \EVOSUITE achieved on the \cuts classes distributed across the \projects
+projects used in the competition is illustrated in Figure~\ref{fig:results30} for a search
+budget of \budgetShort, and in Figure~\ref{fig:results120} for a budget of \budgetLong.
+The median line and branch coverage for the \budgetShort budget is
+\medLinesCoverageRatioShort and \medConditionsCoverageRatioShort, and
+increases to \medLinesCoverageRatioLong and \medConditionsCoverageRatioLong
+for the \budgetLong budget. The median mutation coverage is \SI{0}{\percent} in
+both cases, and equal to all the other tools used in the competition.
 
-\EVOSUITE failed to generate any tests in \numTestGenFailedShort cases with a
-budget of \budgetShort, and in \numTestGenFailedLong cases with a budget of
-\budgetLong. However, we found no crashes of \EVOSUITE itself (e.g., exceptions
-thrown by \EVOSUITE), but in all cases where no tests were generated the
-\EVOSUITE process had been killed by the competition setup, suggesting that
-\EVOSUITE was using more time than allocated.
+As stated in the competition report~\cite{SBFT-toolcomp23} \EVOSUITE is the
+only tool for which the median number of generated tests \emph{decreases}
+from \num{35} for the \budgetShort budget to \num{23.5} for the \budgetLong budget.
+As stated before, \EVOSUITE tries to apply additional post-processing steps to remove
+redundant tests. However, in case of the \budgetShort budget most time is spent on test
+generation and only little time remains for minimisation.
 
-While the results for line coverage and branch coverage are similar, the
-mutation scores are substantially lower. The mutation scores on the \Threeten
-classes are highest compared to the other projects from which classes were taken.
+% While the results for line coverage and branch coverage are similar, the
+% mutation scores are substantially lower. The mutation scores on the \Threeten
+% classes are highest compared to the other projects from which classes were taken.
+
+% https://github.com/JUnitContest/JUGE/blob/master/benchmarktool/src/main/java/sbst/benchmark/Main.java#L160
+In \numTestGenFailedShort cases \EVOSUITE failed to generate any tests with a
+budget of \budgetShort. However, this might have been caused by problems in the
+infrastructure\footnote{https://github.com/JUnitContest/JUGE/}
+of the competition as we found no crashes or error messages
+of \EVOSUITE itself. Instead, the log files contained the error message
+``Error: null'' triggered by line~160 in the \texttt{main()} method of
+the \texttt{sbst.benchmark.Main} class. Here, \EVOSUITE is invoked with an
+\texttt{IBenchmarkTask} object as input which seems to have not been properly
+initialised.
+%
+The same error also ocurred in 13 of \numTestGenFailedLong
+cases with a budget of \budgetLong. In the remaining 4 cases, \EVOSUITE crashed
+with an \texttt{OutOfMemoryError}. % while generating or postprocessing tests.
+
+% threeten-extra-99 (2×)
+% Test generation aborted
+% Out of Memory Error GH overhead limit exceeded
+
+% collections-10
+% Crash
+% java.lang.OutOfMemoryError: Java heap space during test suite minimisation
+
+% ta4j-79
+% java.lang.OutOfMemoryError: GC overhead limit exceeded while post-processing tests
 
@@
 
+As a general trend, participants seem to value expressive names for test cases
+variables, separation of concerns (i.e., unrelated functionality is )
+and meaningful assertions.
+
+shorter tests
+
 \begin{figure}
-  \includegraphics[width=0.9\columnwidth]{./data/understandability}
-  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project.}
+  \includegraphics[width=\columnwidth]{./data/understandability}
+  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project}
   \label{fig:readability}

### 2023-03-15 papers/sbst23/data/main.py

@@ -42,9 +42,9 @@ plot_data = (all_data[columns.keys()]  # (1)
                    value_name='Percent'))  # (3)
 
 """
-Create a boxplot of the EvoSuite data per "Metric" on the x-axis, plotting the 
+Create a boxplot of the EvoSuite data per "Metric" on the x-axis, plotting the
 corresponding values in the "Percent" column on the y-axis. Using "Time Budget"
-as hue key creates grouped a boxplot: for each metric, it actually plots two 
+as hue key creates grouped a boxplot: for each metric, it actually plots two
 boxes for the two budgets.
 """
 utils.preload_latex_style("IEEE")
@@ -136,7 +136,11 @@ utils.save_fig(fig, './CoverageByBenchmark120.pdf')
 
 stats = {
     'score': 678.12,
+    'rank': 1.83,
+    'rankCoverage': 1.79,
+    'rankUnderstandability': 2.23,
     'cuts': all_data['class'].nunique(),
+    'projects': 5,
     'budgetShort': r'\SI{30}{\second}',
     'budgetLong': r'\SI{120}{\second}',
 }
@@ -169,6 +173,7 @@ def test_gen_failed(data):
 
 stats['numTestGenFailedShort'] = test_gen_failed(data30).shape[0]
 stats['numTestGenFailedLong'] = test_gen_failed(data120).shape[0]
+
 
 utils.write_tex_macros('./macros.tex', utils.create_tex_macros(stats))
 

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Fix results section

@@
 
+\begin{figure}
+  \includegraphics[width=\columnwidth]{./data/understandability}
+  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project}
+  \label{fig:readability}
+\end{figure}
+
 For the first time, the competition also conducted a human study with 13
@@
 stating it was ``the most complete'', while another suggested the code
-being longer makes it ``more confusing''.
-
-As a general trend, participants seem to value expressive names for test cases
-variables, separation of concerns (i.e., unrelated functionality is )
-and meaningful assertions.
-
-shorter tests
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{./data/understandability}
-  \caption{Distribution of test case understandability, ranked from 1 (best) to 5 (worst), per project}
-  \label{fig:readability}
-\end{figure}
+being longer makes it ``more confusing''. But as a general trend, participants
+seemed to prefer shorter, more cohesive tests with assertions that only check
+one particular aspect of the method under test.
 

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Update intro

@@
     Passau, Germany \\
-    email address or ORCID
+    sebastian.schweikl@uni-passau.de
   }
@@
     Passau, Germany \\
-    email address or ORCID
+    gordon.fraser@uni-passau.de
   }
@@
   \IEEEauthorblockA{%
-    \textit{Kristiania University College and}\\ \textit{Oslo Metropolitan University} \\
+    \textit{Kristiania University College} and\\ \textit{Oslo Metropolitan University} \\
     Oslo, Norway \\
-    email address or ORCID
+    andrea.arcuri@kristiania.no
   }
@@
 %
-For the last 10 years, the annual unit test generation competition has
-evaluated progress on unit test generation tools using a benchmark of Java
-classes, on which different tools are applied and compared. In the 2023 edition
-of the competition, five tools were applied on a set of \cuts classes. Details
-about the procedure of the competition, the technical framework, and the
-benchmark classes can be found in the competition
-report~\cite{SBFT-toolcomp23}. \EVOSUITE achieved an overall score of \score,
-which was the highest among the competing and baseline tools.
+The aim of the annual Java Unit Testing Competition is to evaluate and monitor
+the progress on automated test generation. To this end, a new corpus of benchmark
+Java classes is created every year, against which various unit test generation tools
+are evaluated. This year, the 11th edition of the competition featured a set of \cuts
+classes, and five tools. Details about the procedure of the competition, the
+technical framework, and the benchmark classes can be found in the competition
+report~\cite{SBFT-toolcomp23}. With an overall score of \score, \EVOSUITE achieved the
+best result among its competitors.
 
@@
 
-The 2023 competition setup was similar to the 2022 setup: The same version of
+The competition setup was similar to the 2022 setup: The same version of
 \EVOSUITE (1.1.0) was used, which by default uses DynaMOSA~\cite{dynamosa} as
@@
 This paper reports on the participation of the \EVOSUITE test generation tool
-in the tenth SBST Java Unit Testing Tool Contest. On average, \EVOSUITE
+in the 11th SBST Java Unit Testing Tool Contest. On average, \EVOSUITE
 achieved \avgConditionsCoverageRatioLong branch coverage,

### 2023-03-15 papers/sbst23/paper_sbst23.tex
WIP: About EvoSuite

@@
 
-\EVOSUITE~\cite{FrA11c} automatically generates test suites for Java classes
-using evolutionary search. As input \EVOSUITE only requires the name of the
-target class as well as the classpath on which the compiled bytecode of the
-target class and its dependencies are located. \EVOSUITE first extracts
-information about the relevant classes as well as their constructors, methods,
-and fields using a basic static analysis. It instruments the bytecode while
-classes are loaded by the Java classloader, such that \EVOSUITE can produce
-execution traces for test executions, and to avoid test flakiness by replacing
-non-deterministic calls with deterministic, mocked versions. Finally, \EVOSUITE
-applies meta-heuristic search algorithms to automatically produce JUnit test
-cases aimed at maximising code coverage.
-%Besides the basic command line interface there are also plugins for popular development environments such as IntelliJ, Eclipse, or Maven~\cite{ICST16_Tool}.
+\EVOSUITE~\cite{FrA11c} is an automatic test generation tool for Java classes.
+It takes the name of the target class as input, along with a Java classpath that
+locates the class's compiled bytecode and that of its dependencies, and produces
+a test suite in JUnit~4 format as output.
 
-\EVOSUITE generates tests using evolutionary algorithms.
-%
-For this, it uses a genetic encoding of test cases consisting of variable-length sequences of Java statements (e.g., primitive statements as well as calls on constructors or methods).
-Standard evolutionary search operators (e.g., selection, crossover, mutation) are adapted for this representation.
-%
-\EVOSUITE provides several different evolutionary algorithms to operate on this
+In a preprocessing phase, \EVOSUITE uses a basic static analysis to collect
+information about the relevant classes, such as their constructors, methods
+and fields. \EVOSUITE loads these classes into the Java Virtual Machine, and
+applies various bytecode instrumentations while doing so. This enables \EVOSUITE
+to produce test execution traces, and to avoid test flakiness by replacing
+non-deterministic calls with deterministic, mocked versions.
+
+The main execution phase of \EVOSUITE is dedicated to test generation. Here,
+meta-heuristic search algorithms are applied to automatically produce JUnit
+tests that maximise code coverage. Internally, \EVOSUITE uses a genetic encoding
+that represents a test case as variable-length sequence of Java statements
+(e.g., primitive statements as well as calls on constructors or methods).
+Standard evolutionary search operators (e.g., selection, crossover, mutation)
+are adapted for this representation.
+
+\EVOSUITE implements various evolutionary algorithms that operate on this
 representation. The initial approach was to optimise entire test suites with
@@
 algorithm~\cite{dynamosa}, which operates at the test case level.
-%
+
 The search is driven by fitness functions that encode coverage criteria.
-\EVOSUITE can optimise for several criteria simultaneously, and the core fitness functions in \EVOSUITE are based on traditional heuristics for code coverage, such as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details).
-However, there are several further fitness functions based on mutation testing~\cite{emse14_mutation} as well as other basic criteria~\cite{rojas2015combining}.
+\EVOSUITE can optimise for several criteria simultaneously, and the core fitness
+functions in \EVOSUITE are based on traditional heuristics for code coverage, such
+as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details).
+However, there are several further fitness functions based on mutation
+testing~\cite{emse14_mutation} as well as other basic
+criteria~\cite{rojas2015combining}.
 
@@
 
-\EVOSUITE is also heavily optimised in order to produce tests that are as readable as possible and avoid test smells~\cite{panichella2020revisiting}.
-For this, \EVOSUITE applies post-processing once the available search budget has been exhausted~\cite{FrA11c,FrA13a}, consisting of minimisation to remove redundant tests and statements, and adding a minimised set of assertions using mutation analysis~\cite{10.1109/TSE.2011.93}.
-%Besides multiple in-depth empirical evaluations of \EVOSUITE with respect to
-%code coverage~\cite{fraser2014large,emse_archive,ea_evaluation,dynamosa},
-%fault-finding effectiveness~\cite{shamshiri2015automatically,moein2017}, and
-%effects on developer productivity~\cite{TOSEM_userstudy,ISSTA15_Study} and
-%software maintenance~\cite{ICST2018_Maintenance}, \EVOSUITE has also participated in all prior instances of the unit testing tool competition, usually ranking among the best performing tools.
+\EVOSUITE is also heavily optimised in order to produce tests that are as
+readable as possible and avoid test smells~\cite{panichella2020revisiting}.
+For this, \EVOSUITE applies post-processing once the available search budget
+has been exhausted~\cite{FrA11c,FrA13a}, consisting of minimisation to
+remove redundant tests and statements, and adding a minimised set of assertions
+using mutation analysis~\cite{10.1109/TSE.2011.93}.
 
@@
 % No new features were added in this version, but support
-% for Java 9+ was added, several bugs were fixed, and amajor refactoring was applied
+% for Java 9+ was added, several bugs were fixed, and a major refactoring was applied
 % to improve the code quality with respect to the

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Rest of About EvoSuite section

@@
 \EVOSUITE implements various evolutionary algorithms that operate on this
-representation. The initial approach was to optimise entire test suites with
-respect to their overall code coverage~\cite{GoA_TSE12}. However, after
-extensive evaluation~\cite{ea_evaluation} the default is now the
-\emph{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA) search
-algorithm~\cite{dynamosa}, which operates at the test case level.
+representation. Early versions of \EVOSUITE followed the \emph{Whole Test Suite} (WTS)
+approach~\cite{GoA_TSE12}, where entire test suites are optimised with
+respect to their overall code coverage. However, a subsequent study~\cite{ea_evaluation}
+found the \emph{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA)~\cite{dynamosa}
+to yield superior results. Unlike WTS, DynaMOSA operates directly at the test case level,
+and it is now the default algorithm in \EVOSUITE.
 
-The search is driven by fitness functions that encode coverage criteria.
-\EVOSUITE can optimise for several criteria simultaneously, and the core fitness
-functions in \EVOSUITE are based on traditional heuristics for code coverage, such
-as the branch distance and the approach level (see~\cite{GoA_TSE12} for more details).
-However, there are several further fitness functions based on mutation
-testing~\cite{emse14_mutation} as well as other basic
-criteria~\cite{rojas2015combining}.
+Irrespective of which algorithm is chosen, the search is always driven by fitness
+functions. These encode coverage criteria, and \EVOSUITE can optimise for multiple
+criteria at the same time. Core fitness functions are based on traditional heuristics
+for code coverage, such as branch distance and approach level (see ~\cite{GoA_TSE12} for more details.)
+Besides this, there are further fitness functions based on mutation
+testing~\cite{emse14_mutation} and other basic criteria~\cite{rojas2015combining}.
 
@@
 
-\EVOSUITE is also heavily optimised in order to produce tests that are as
-readable as possible and avoid test smells~\cite{panichella2020revisiting}.
-For this, \EVOSUITE applies post-processing once the available search budget
-has been exhausted~\cite{FrA11c,FrA13a}, consisting of minimisation to
-remove redundant tests and statements, and adding a minimised set of assertions
-using mutation analysis~\cite{10.1109/TSE.2011.93}.
+Once the available search budget for the main phase has been exhausted,
+\EVOSUITE can be configured to run a postprocessing phase where tests are optimised for
+readability~\cite{FrA11c,FrA13a}. This includes avoiding test
+smells~\cite{panichella2020revisiting}, minimisation to remove redundant tests
+and statements, and adding a minimised set of assertions using mutation
+analysis~\cite{10.1109/TSE.2011.93}.
 

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Pass over Competition Setup

@@
 
-The competition setup was similar to the 2022 setup: The same version of
-\EVOSUITE (1.1.0) was used, which by default uses DynaMOSA~\cite{dynamosa} as
-the search algorithm.
+\EVOSUITE is currently undergoing a significant rewrite to improve the quality
+of its internal code base, for example a better use of Java generics to aid
+type safety. The latest version (1.2.0) contains the first fruits of this effort,
+but also introduced regressions that still existed at the time the competition was
+hold. For this reason, the same version (1.1.0) as in previous years was used.
+The remaining setup was largely similar to the 2022 iteration: DynaMOSA~\cite{dynamosa}
+was chosen as search algorithm, and \EVOSUITE was configured with the parameters
+established in prior years, which mainly uses the tuned default
+values~\cite{arcuri2013parameter} and default coverage criteria~\cite{rojas2015combining}.
+%
 % No new features were added in this version, but support
@@
 % applied for 2022.
-
-The configuration is largely identical to the established configuration used in
-prior years, and mainly uses the tuned default
-values~\cite{arcuri2013parameter} and default coverage criteria
-\cite{rojas2015combining}.
 %
-Unlike previous years, where the competition score did not yet reward readability,
-the configuration now enables a test minimisation step, and filters regression
-assertions using mutation analysis.
+However, in previous years the competition only rewarded code coverage, and this year
+test case readability is also factored in. To account for this, configuration now
+enables a test minimisation step, and filters regression assertions using mutation analysis.
 %
@@
 
-With an overall score of \score \EVOSUITE was the highest ranking tool
+With an overall score of \score, \EVOSUITE was the highest ranking tool
 (rank \rank) in the competition. The score is computed as the weighted

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Add TODOs
Add missing TODO

@@
 \newif\ifdraft
-\draftfalse
+%\draftfalse
+\drafttrue
 
@@
 \begin{abstract}
+  \TODO{Reword}
   \EVOSUITE is a search-based unit test generation tool for Java.
@@
 
+\TODO{rephrase this paragraph}
 A large share of the complexity of \EVOSUITE's code base is due to efforts to
@@
 
+\TODO{Update and Reword}
 This paper reports on the participation of the \EVOSUITE test generation tool

### 2023-03-15 papers/sbst23/paper_sbst23.tex
Pass over paper

--- 2023-03-15 papers/sbst23/paper_sbst23.tex
@@
 \begin{abstract}
-  \EVOSUITE is a search-based unit test generation tool for Java.
-This paper summarises the results and experiences of \EVOSUITE's participation at the 11th unit testing competition at SBFT 2023, where \EVOSUITE achieved the highest overall score.
+  \EVOSUITE is an automated unit test generation tool for Java based
+  on meta-heuristic search techniques. This paper summarises the
+  results and experiences of \EVOSUITE's participation at the 11th
+  unit testing competition at SBFT 2023, where \EVOSUITE achieved the
+  highest overall score.
 \end{abstract}
@@
 locates the class's compiled bytecode and that of its dependencies, and produces
-a test suite in JUnit~4 format as output.
+a test suite in JUnit~4 format optimised for code coverage as output.
 
@@
 and fields. \EVOSUITE loads these classes into the Java Virtual Machine, and
-applies various bytecode instrumentations while doing so. This enables \EVOSUITE
+applies various types of  bytecode instrumentation while doing so. This enables \EVOSUITE
 to produce test execution traces, and to avoid test flakiness by replacing
@@
 
-\EVOSUITE implements various evolutionary algorithms that operate on this
+\EVOSUITE implements several different evolutionary algorithms that operate on this
 representation. Early versions of \EVOSUITE followed the \emph{Whole Test Suite} (WTS)
 approach~\cite{GoA_TSE12}, where entire test suites are optimised with
-respect to their overall code coverage. However, a subsequent study~\cite{ea_evaluation}
-found the \emph{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA)~\cite{dynamosa}
+respect to their overall code coverage. A subsequent study~\cite{ea_evaluation}
+introduced the \emph{Dynamic Many-Objective Sorting Algorithm} (DynaMOSA)~\cite{dynamosa} algorithm, which was shown
 to yield superior results. Unlike WTS, DynaMOSA operates directly at the test case level,
@@
 criteria at the same time. Core fitness functions are based on traditional heuristics
-for code coverage, such as branch distance and approach level (see ~\cite{GoA_TSE12} for more details.)
+for code coverage, such as branch distance and approach level (see \EVOSUITE's original paper~\cite{GoA_TSE12} for more details.)
 Besides this, there are further fitness functions based on mutation
@@
 
-A large share of the complexity of \EVOSUITE's code base is due to efforts to
-avoid flakiness in the generated tests. On the one hand, this covers extensive
-instrumentation and mocking. On the other hand, \EVOSUITE also compiles and
-executes each test individually to avoid compilation errors (which may be the
-result of bugs in \EVOSUITE) or flakiness caused by non-determinism in the
+\EVOSUITE consists of a large code base, of which a large share is
+dedicated to avoiding flakiness in the generated tests. This is
+achieved using extensive instrumentation and mocking, as well as
+post-processing; for example, \EVOSUITE compiles and executes each
+test individually to avoid compilation errors (which may be the result
+of bugs in \EVOSUITE) or flakiness caused by non-determinism in the
 class under test.
@@
 %
-However, in previous years the competition only rewarded code coverage, and this year
-test case readability is also factored in. To account for this, configuration now
+While in previous years the competition only rewarded code coverage, this year
+test case readability was also factored in. To account for this, the new configuration 
 enables a test minimisation step, and filters regression assertions using mutation analysis.
@@
 
-For the first time, the competition also conducted a human study with 13
+For the first time, the competition included a human study with 13
 participants to assess test case readability. For each of the projects \Collections,
@@
 on a scale from 1 (best) to 5 (worst), in terms of readability. Overall,
-\EVOSUITE achieved the 2nd best rating (rank 2.23 on average), only
+\EVOSUITE achieved the 2nd best rating (rank 2.23 on average), 
 preceded by \UtbotConcolic (2.13 on average). \EVOSUITE's rank distribution
@@
 \EVOSUITE ranked best, they positively highlighted the thoroughness of
-generated assertions, using edge cases as inputs, and the fact that tests
-where short. When \EVOSUITE ranked worst, participants criticised the lack
-of comments and descriptive test names, repetitiveness in the code, and
-needless assertions. While \EVOSUITE's competition setup enabled test and
-assertion minimisation, this is a computationally very expensive process,
-and it is likely \EVOSUITE was sometimes unable to finish in time,
-leaving tests unoptimised.
+generated assertions, using edge cases as inputs, and the fact that
+tests where short. When \EVOSUITE ranked worst, participants
+criticised the lack of comments and descriptive test names,
+repetitiveness in the code, and needless assertions. While \EVOSUITE's
+competition setup enabled test and assertion minimisation, this is a
+computationally very expensive process, and it is likely \EVOSUITE was
+sometimes unable to finish in time, leaving tests unoptimised. In
+particilar, there are two aspects of this minimisation: The first
+minimisation phase attempts to remove all statements in a test that
+are irrelevant for achieving the test's coverage goals; the second
+minimisation phase consists of selecting a minimal subset of test
+assertions that are sufficient to detect all code mutants the test is
+capable of detecting. If either of these phases exceeds the allocated
+time budget it is cancelled, and \EVOSUITE returns the non-minimised
+tests.
 
-Among the tests for \Collections the longest one was produced by \EVOSUITE.
-Interestingly, it ranked both highest and lowest, with one participant
-stating it was ``the most complete'', while another suggested the code
-being longer makes it ``more confusing''. But as a general trend, participants
-seemed to prefer shorter, more cohesive tests with assertions that only check
-one particular aspect of the method under test.
+Among the tests for \Collections the longest one was produced by
+\EVOSUITE.  Interestingly, it ranked both highest and lowest, with one
+participant stating it was ``the most complete'', while another
+suggested the code being longer makes it ``more confusing''. As a
+general trend, participants seemed to prefer shorter, more cohesive
+tests with assertions that only check one particular aspect of the
+method under test.
 
@@
 
-This paper reports on the participation of the \EVOSUITE test generation tool
-in the 11th SBST Java Unit Testing Tool Contest. On average, \EVOSUITE
-achieved \avgConditionsCoverageRatioLong branch coverage,
-\avgLinesCoverageRatioLong line coverage, and a mutation score of
-\avgMutantsCoverageRatioLong, using a search budget of \budgetLong on the \cuts
-classes considered for the competition. Overall, this results in a score of
-\score, which is the highest score of all tools in the competition.
+This paper describes the results and experiences of \EVOSUITE's
+participation in the 11th SBST Java Unit Testing Tool Contest. On
+average, \EVOSUITE achieved \avgConditionsCoverageRatioLong branch
+coverage, \avgLinesCoverageRatioLong line coverage, and a mutation
+score of \avgMutantsCoverageRatioLong, using a search budget of
+\budgetLong on the \cuts classes considered for the
+competition. Overall, this results in a score of \score, which is the
+highest score of all competing tools.
 
@@
 %\clearpage
+\balance
 \bibliographystyle{IEEEtranS}
 \bibliography{papers}
-\balance
 

### 2023-03-15 papers/sbst23/paper_sbst23.tex
fix(results): mention average coverage instead of median coverage

@@
 budget of \budgetShort, and in Figure~\ref{fig:results120} for a budget of \budgetLong.
-The median line and branch coverage for the \budgetShort budget is
-\medLinesCoverageRatioShort and \medConditionsCoverageRatioShort, and
-increases to \medLinesCoverageRatioLong and \medConditionsCoverageRatioLong
-for the \budgetLong budget. The median mutation coverage is \SI{0}{\percent} in
-both cases, and equal to all the other tools used in the competition.
+The average line and branch coverage for the \budgetShort budget is
+\avgLinesCoverageRatioShort and \avgConditionsCoverageRatioShort, and
+increases to \avgLinesCoverageRatioLong and \avgConditionsCoverageRatioLong
+for the \budgetLong budget. The average mutation coverage is \avgMutantsCoverageRatioShort
+and \avgMutantsCoverageRatioLong, respectively.
 
